---
title: "DST analyses"
author: "Logan Schneider"
date: "August 5, 2018"
output: html_document
---

    ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown  
```{r FYI, echo=FALSE}
#print("Analyses perfomed using:")
#R.Version()$version.string
print("lubridate,zoo,ggplot2,RColorBrewer,car,agricolae")
library(lubridate)
library(zoo)
library(ggplot2)
library(RColorBrewer)
library(car)
library(agricolae)
library(scales)
library(effsize) #for effect size estimates
library(weights) #for weighted stats
library(SDMTools) #for weighted stats
print("Please use the following citation information")
citation()

sessionInfo()
```
  
Data loading  
#perform after DSTclean.Rmd preprocessing complete  
#=====================================#
```{r Data loading}
#to read in the saved csv files:
Sz08to16 <- read.csv("Sz08to16wInc&RelRates.csv", stringsAsFactors = F)
Sz08to16 <- Sz08to16[,-1]
Sz08to16$datetime <- as.POSIXct(Sz08to16$datetime)
print(paste("After cleaning, there remain",
            length(unique(Sz08to16$Unlinked_ID)),
            "individuals and",
            nrow(Sz08to16),
            "seizures."))

#Are the DST onset days correctly identified?
table(as.Date(Sz08to16[which(Sz08to16$DSTonday == 0),"datetime"])) #Yes

Day08to16 <- read.csv("DAY08to16wInc&RelRates.csv", stringsAsFactors = F)
Day08to16 <- Day08to16[,-1]
Day08to16$datetime <- as.POSIXct(Day08to16$datetime)

Night08to16 <- read.csv("NIGHT08to16wInc&RelRates.csv", stringsAsFactors = F)
Night08to16 <- Night08to16[,-1]
Night08to16$datetime <- as.POSIXct(Night08to16$datetime)
```
  
  
Data imaging and analysis 
#====================================#  
```{r yearly data summaries}
#examine by year; source method: http://stackoverflow.com/questions/2127926/how-do-i-highlight-an-observations-bin-in-a-histogram-in-r
highlight <- function(x, value1, value2, col.value1, col.value2, col=NA, ...){
    hst <- hist(x, ...)
    idx1 <- findInterval(value1, hst$breaks)
    idx2 <- findInterval(value2, hst$breaks)
    cols <- rep(col, length(hst$counts))
    cols[idx1] <- col.value1
    cols[idx2] <- col.value2
    hist(x, col=cols, ...)
}

ordered <- Sz08to16[with(Sz08to16, order(Unlinked_ID, datetime)), ]
#weeks are funny at the start and end of the year with partial weeks, so remove them
orderednotails <- ordered[which(epiweek(ordered$datetime) > 1 & epiweek(ordered$datetime) < 52),"datetime"]
summary(epiweek(orderednotails))

for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    DSTon <- as.Date(ymd(paste(i,3,01,sep="-")))
    DSTon <- as.Date(ifelse(wday(DSTon)==1,DSTon+7,DSTon+(15-wday(DSTon))))
    DSToff <- as.Date(ymd(paste(i,11,01,sep="-")))
    DSToff <- as.Date(ifelse(wday(DSToff)==1,DSToff,DSToff+(8-wday(DSToff))))
    #Szwks <- epiweek(ordered[which(year(ordered$datetime)==i),"datetime"])
    #highlight(Szwks,epiweek(DSTon),epiweek(DSToff),"red","blue",breaks=week(as.POSIXct(paste(i,12,31,sep="-"))),main=paste("Histogram of seizure counts for ",i,sep=""))
    Szwks <- epiweek(orderednotails[which(year(orderednotails)==i)])
    highlight(Szwks,
              epiweek(DSTon),
              epiweek(DSToff),
              "red",
              "blue",
              breaks=51,
              main=paste("Histogram of seizure counts for ",i,sep=""))
}

#plot aggregate data from complete years: 2008-2016
#-normalize week of DST transition to 0
#Szwks<-epiweek(Sz08to16[,"datetime"])-Sz08to16[,"DSTweek"]
Szwks<-epiweek(Sz08to16[which(epiweek(Sz08to16$datetime) > 1 & epiweek(Sz08to16$datetime) < 52),"datetime"])-Sz08to16[which(epiweek(Sz08to16$datetime) > 1 & epiweek(Sz08to16$datetime) < 52),"DSTweek"]
#-plot with highlights
#highlight(Szwks,0,34,"red","blue",breaks=53,main="Histogram of seizure counts for Jan 2008-Dec 2016")
highlight(Szwks,0,34,"red","blue",breaks=51,main="Histogram of seizure counts for Jan 2008-Dec 2016")
```
  
Subsetting datasets for DST and baseline time windows  
```{r data subsetting}
#Make relevant dataframes for comparison:
#-the week of DST (DSTonday 0-6: Sun-Sat)
Sz08to16wkofDST <- Sz08to16[which(Sz08to16$DSTonday >= 0 & Sz08to16$DSTonday < 7),] #only includes DST-week days
#Sz08to16wkofDST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$DSTweek),] 
summary(Sz08to16wkofDST$DSTonday)
wkofDST <- table(Sz08to16wkofDST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkofDST[recombobulate])
str(Sz08to16wkofDST$DSTonday)
#-the week before DST (a control time period)
Sz08to16wkpreDST <- Sz08to16[which((yday(Sz08to16$datetime) >= Sz08to16$DSTday-7 ) & (yday(Sz08to16$datetime) < Sz08to16$DSTday-0 ) ),] #only includes days in week before DST
#Sz08to16wkpreDST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$DSTweek-1),] 
summary(yday(Sz08to16wkpreDST$datetime))
summary(Sz08to16$DSTday)
wkpreDST <- table(Sz08to16wkpreDST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkpreDST[recombobulate])
str(yday(Sz08to16wkpreDST$datetime))
#-the week following DST week (a control time period)
Sz08to16wkpostDST <- Sz08to16[which(Sz08to16$DSTonday >= 7 & Sz08to16$DSTonday < 14),] #only includes days in week following DST week
#Sz08to16wkpostDST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$DSTweek+1),] 
summary(yday(Sz08to16wkpostDST$datetime))
summary(Sz08to16$DSTday)
wkpostDST <- table(Sz08to16wkpostDST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkpostDST[recombobulate])
str(yday(Sz08to16wkpostDST$datetime))
#-the week of ST (STonday 0-6: Sun-Sat) (a control time period, or primary time period)
Sz08to16wkofST <- Sz08to16[which(Sz08to16$DSToffday >= 0 & Sz08to16$DSToffday < 7),] #only includes ST-week days
#Sz08to16wkofST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$STweek),] 
summary(Sz08to16wkofST$DSToffday)
wkofST <- table(Sz08to16wkofST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkofST[recombobulate])
str(Sz08to16wkofST$DSToffday)
#-the week before ST (a control time period)
Sz08to16wkpreST <- Sz08to16[which(Sz08to16$DSTonday > 231 & Sz08to16$DSTonday <= 238),] #only includes days in week before ST week
#Sz08to16wkpreST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$STweek-1),] 
summary(yday(Sz08to16wkpreST$datetime))
summary(Sz08to16$STday)
wkpreST <- table(Sz08to16wkpreST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkpreST[recombobulate])
str(yday(Sz08to16wkpreST$datetime))
#-the week following ST week (a control time period)
Sz08to16wkpostST <- Sz08to16[which(Sz08to16$DSToffday >= 7 & Sz08to16$DSToffday < 14),] #only includes days in week following ST week
#Sz08to16wkpostST <- Sz08to16[which(epiweek(Sz08to16$datetime) == Sz08to16$STweek+1),] 
summary(yday(Sz08to16wkpostST$datetime))
summary(Sz08to16$STday)
wkpostST <- table(Sz08to16wkpostST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(wkpostST[recombobulate])
str(yday(Sz08to16wkpostST$datetime))
#-NOT week of DST (a control time period)
Sz08to16notDST <- Sz08to16[which(Sz08to16$DSTonday >= 7 | Sz08to16$DSToffday >=0),] #includes all non-DST-week days and all ST days
#Sz08to16notDST <- Sz08to16wkofDST <- Sz08to16[which(epiweek(Sz08to16$datetime) != Sz08to16$DSTweek),] 
summary(yday(Sz08to16notDST$datetime))
notDST <- table(Sz08to16notDST$wkday)
recombobulate <- c(4,2,6,7,5,1,3) #needed to reorder the alphabetical ordering default of table
barplot(notDST[recombobulate])
str(yday(Sz08to16notDST$datetime))
```
  
Comparisons to baseline windows  
###ANALYZED AS SO: chi square by day of the week, T-test (two tailed) by average day of the week, ORs  
```{r initial comparisons for chi-square}
DSTvsPRE <- data.frame("wkofDST"=as.data.frame(wkofDST[recombobulate])[,2],"wkpreDST"=as.data.frame(wkpreDST[recombobulate])[,2])
rownames(DSTvsPRE) <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
chisq.test(DSTvsPRE)
barplot(t(DSTvsPRE),legend=T,beside=T)

DSTvsST <- data.frame("wkofDST"=as.data.frame(wkofDST[recombobulate])[,2],"wkofST"=as.data.frame(wkofST[recombobulate])[,2])
rownames(DSTvsST) <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
chisq.test(DSTvsST)
barplot(t(DSTvsST),legend=T,beside=T)
```
  
Calculate Z-scores and percentile for DST seizure mean using the whole of population data as the "normative baseline"  
```{r zscore comparisons and independent t-tests comparing DST to any non-DST baseline weekday}
dailypercentiles <- data.frame("Weekday"=character(),
                               "MeanPercentile"=numeric(),
                               "PercentileSD"=numeric(),
                               stringsAsFactors = F)
sigdf <- data.frame("Weekday"=character(),
                    "p"=numeric(),
                    "p.signif"=character(),
                    stringsAsFactors = F)
percentalls <- data.frame("Year"=numeric(),
                          "Percentile"=numeric(),
                          "Weekday"=character(),
                          stringsAsFactors = F)
yearlist <- c(min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) #Bound years by the bounds of the dataset
list <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
index=1
for(i in list) {
    yearlyDSTdf <- data.frame("Year"=numeric(),
                              "PopMean"=numeric(),
                              "PopSD"=numeric(),
                              "SzCount"=numeric(),
                              "Zscore"=numeric(),
                              "Percentile"=numeric())
    counter=1
    for(j in yearlist) {
        daymean <- mean(table(as.Date(Sz08to16[which(Sz08to16$wkday == i & year(Sz08to16$datetime) == j),"datetime"],
                                      'America/Los_Angeles')))
        yearlyDSTdf[counter,"PopMean"] <- daymean
        daysd <- sd(table(as.Date(Sz08to16[which(Sz08to16$wkday == i & year(Sz08to16$datetime) == j),"datetime"],
                                  'America/Los_Angeles')))
        yearlyDSTdf[counter,"PopSD"] <- daysd
        yearlyDSTdf[counter,"Year"] <- j
        yearlyDSTdf[counter,"SzCount"] <- table(as.Date(Sz08to16wkofDST[which(Sz08to16wkofDST$wkday == i & year(Sz08to16wkofDST$datetime) == j),"datetime"],
                                                        'America/Los_Angeles'))[[1]]
        yearlyDSTdf[counter,"Zscore"] <- (yearlyDSTdf[counter,"SzCount"] - daymean)/daysd
        yearlyDSTdf[counter,"Percentile"] <- round(pnorm(yearlyDSTdf[counter,"Zscore"])*100,2)
        counter=counter+1
    }
    FORtall <- yearlyDSTdf[,c("Year","Percentile")]
    FORtall$Weekday <- i
    percentalls <- rbind(percentalls,FORtall)
    write.table(yearlyDSTdf,
                file = paste(i,"yearly percentiles.txt"),
                quote = F,
                row.names = F)
    
    dailypercentiles[index,"Weekday"] <- i
    dailypercentiles[index,"MeanPercentile"] <- mean(yearlyDSTdf$Percentile)
    dailypercentiles[index,"PercentileSD"] <- sd(yearlyDSTdf$Percentile)/sqrt(max(year(Sz08to16$datetime))-min(year(Sz08to16$datetime)))
    
    sigdf[index,"Weekday"] <- i
    #sigdf[index,"p"] <- round(t.test(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')),
    #                                 table(as.Date(secondweek[which(secondweek$wkday == i),"datetime"],'America/Los_Angeles')))[["p.value"]],4)
    sigdf[index,"p"] <- round(t.test(table(as.Date(Sz08to16wkofDST[which(Sz08to16wkofDST$wkday == i),"datetime"],'America/Los_Angeles')),
                                     table(as.Date(Sz08to16notDST[which(Sz08to16notDST$wkday == i),"datetime"],'America/Los_Angeles')))[["p.value"]],4)
    if(sigdf[index,"p"]<0.05 & sigdf[index,"p"]>0.01) {
        sigdf[index,"p.signif"] <- "*"
    } else if(sigdf[index,"p"]<0.01 & sigdf[index,"p"]>0.001) {
        sigdf[index,"p.signif"] <- "**"
    } else if(sigdf[index,"p"]<0.001) {
        sigdf[index,"p.signif"] <- "***"
    } else {
        sigdf[index,"p.signif"] <- "ns"
    }
    
    index=index+1
}
dailypercentiles$Weekday <- factor(dailypercentiles$Weekday, levels = dailypercentiles$Weekday) #ensures weekdays stay in order Sun-Sat
dailypercentiles
factorlevels <- factor(list,levels=list)
percentalls$Weekday <- factor(percentalls$Weekday, levels=factorlevels) #ensures weekdays stay in order Sun-Sat

#library(ggplot2)

print(ggplot(dailypercentiles, aes(x=Weekday, y=MeanPercentile)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3,  # Thinner lines
             alpha=0.8) +  #Semi-transparent
    #stat_compare_means(aes(group = Week), label = "p.signif", label.y = 300)
    geom_errorbar(aes(ymin=MeanPercentile-PercentileSD, ymax=MeanPercentile+PercentileSD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    geom_point(data=percentalls, aes(x=Weekday, y=Percentile, color=factor(Year)), size=3, alpha=0.8) + 
    xlab("Weekday") +
    ylab("Percentile (\u00b1SEM)") +
    ggtitle(paste("Percentile of DST seizure counts by weekday over period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
    scale_y_continuous(breaks=0:100*10, limits=c(0,100)) +
    theme_bw() + 
    theme(legend.title = element_blank()))
png(paste("Percentile of DST seizure counts by weekday over period from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(dailypercentiles, aes(x=Weekday, y=MeanPercentile)) + 
    geom_bar(position=position_dodge(), stat="identity",
             colour="black", # Use black outlines,
             size=.3,  # Thinner lines
             alpha=0.8) +  #Semi-transparent
    #stat_compare_means(aes(group = Week), label = "p.signif", label.y = 300)
    geom_errorbar(aes(ymin=MeanPercentile-PercentileSD, ymax=MeanPercentile+PercentileSD),
                  size=.3,    # Thinner lines
                  width=.2,
                  position=position_dodge(.9)) +
    geom_point(data=percentalls, aes(x=Weekday, y=Percentile, color=factor(Year)), size=3, alpha=0.8) + 
    xlab("Weekday") +
    ylab("Percentile (\u00b1SEM)") +
    ggtitle(paste("Percentile of DST seizure counts by weekday over period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
    scale_y_continuous(breaks=0:100*10, limits=c(0,100)) +
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
```
  
Check seizure weekday percentiles for DST by ANOVA
```{r ANOVA of DST percentiles by weekday}
attach(percentalls)
Anova(lm(Percentile ~ Weekday,
         data=percentalls),
      type="III")
wkday2percentile <- aov(lm(Percentile ~ Weekday))
wkday2percentile
posthoc <- TukeyHSD(x=wkday2percentile, 'Weekday', conf.level = 0.95)
posthoc
hsdwkday2percentile <- HSD.test(wkday2percentile, "Weekday")
hsdwkday2percentile
```
It appears that Saturday is in a group all it's own (by DST percentiles)...and that it's somewhat protective  
Also, the periweekend days (Fri, Sat, and Sun) appear to be somewhat distinct as well  
  
###Is the "Weekend protective effect" present throughout the year?  
```{r weekday counts for the whole dataset}
weekendlist <- c("Wednesday","Thursday","Friday","Saturday","Sunday","Monday","Tuesday")
#factorlevels <- factor(list,levels=weekendlist) 
factorlevels <- factor(weekendlist, levels = weekendlist) # setting factor levels to put weekend in middle of graphs
#wkdayrefactored <- Sz08to16
#wkdayrefactored$wkday <- factor(wkdayrefactored$wkday, levels=factorlevels)
#totANOVA <- as.data.frame(table(wkdayrefactored$wkday))
totANOVA <- as.data.frame(table(Sz08to16$wkday))
totANOVA$Var1 <- factor(totANOVA$Var1, levels=factorlevels)
#Just take a look at total seizure counts over the whole period

print(ggplot(totANOVA, aes(x=Var1, y=Freq)) + 
    geom_histogram(stat="identity") +
    xlab("Weekday") + 
    ylab("Total seizure counts") + 
    scale_y_continuous(breaks = c(round(min(totANOVA$Freq),digits=-3),round(max(totANOVA$Freq),digits=-3))) + 
    #ylim(round(min(totANOVA$Freq),digits=-3),round(max(totANOVA$Freq),digits=-3)) +
    ggtitle(paste("Total weekday seizure counts over",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) + 
    theme_bw() + 
    theme(legend.position = "none"))

print(ggplot(totANOVA, aes(x=Var1, y=Freq)) + 
    geom_point(size=3) +
    ylab("Total seizure counts") +
    ggtitle(paste("Total weekday seizure counts over",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) + 
    theme_bw() + 
    theme(legend.position = "none",
          axis.title.x = element_blank()))

png("Weekday count totals from entire dataset.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(totANOVA, aes(x=Var1, y=Freq)) + 
    geom_point(size=3) +
    ylab("Total seizure counts") +
    ggtitle(paste("Total weekday seizure counts over",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) + 
    theme_bw() + 
    theme(legend.position = "none",
          axis.title.x = element_blank()))
dev.off()
```
Seems like there might be a protective pattern for the weekends  
  
#First check ANOVA by yearly counts as a coarse estimate  
```{r ANOVA by yearly count totals for each weekday}
tabling <- Sz08to16[,c("wkday","datetime")]
tabling$datetime <- year(tabling$datetime)
tabling$wkday <- factor(tabling$wkday, levels=factorlevels)
table(tabling)
#barplot(table(tabling),
#        col=brewer.pal(n=7,"Accent"),
#        legend.text=T,
#        args.legend=list(x="topleft"),
#        beside=T)
par(mar = c(5,4,4,8))
barplot(table(tabling),
        col=brewer.pal(n=7,"Accent"),
        legend.text=T,
        args.legend = list(x = "right", bty="n", inset=c(-0.3,0), xpd = TRUE),
        ylab = "Total seizure counts per weekday",
        beside=T)
png(paste("Weekday count totals from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
par(mar = c(5,4,4,8))
barplot(table(tabling),
        col=brewer.pal(n=7,"Accent"),
        legend.text=T,
        args.legend = list(x = "right", bty="n", inset=c(-0.3,0), xpd = TRUE),
        ylab = "Total seizure counts per weekday",
        beside=T)
dev.off()

#Now doing it by proportion:

#Legend location: https://coders-corner.net/2016/03/06/data-visualization-in-r-show-legend-outside-of-the-plotting-area/
par(mar = c(5,4,4,8))
barplot(prop.table(table(tabling),margin=2),
        col=brewer.pal(n=7,"Accent"),
        legend.text=T,
        args.legend = list(x = "right", bty="n", inset=c(-0.3,0), xpd = TRUE),
        ylab = "Proportion of yearly seizure counts",
        beside=T)
png(paste("Weekday count proportions from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
par(mar = c(5,4,4,8))
barplot(prop.table(table(tabling),margin=2),
        col=brewer.pal(n=7,"Accent"),
        legend.text=T,
        args.legend = list(x = "right", bty="n", inset=c(-0.3,0), xpd = TRUE),
        ylab = "Proportion of yearly seizure counts",
        beside=T)
dev.off()

yearANOVA <- as.data.frame(table(tabling))
attach(yearANOVA)
wANOVA <- Anova(lm(Freq ~ wkday,
                data=yearANOVA),
                type="III")
print(wANOVA)
day2countYEAR <- aov(lm(Freq ~ wkday))
day2countYEAR
posthoc <- TukeyHSD(x=day2countYEAR, 'wkday', conf.level = 0.95)
posthoc
hsdday2countYEAR <- HSD.test(day2countYEAR, "wkday")
hsdday2countYEAR
```
Based on looking at those yearly counts, still seems like a plausible hypothesis  
  
#Now check ANOVA by weekly counts (more granular and less subject to varying/accruing subject counts over the year)  
```{r ANOVA by weekly counts in each year}
tabling <- Sz08to16[,c("wkday","weeknum")]
summary(tabling)
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
tabling <- tabling[which(tabling$weeknum > 1 & tabling$weeknum < 52),]
summary(tabling)

summary(Sz08to16$weeknum)
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
FORtabling <- Sz08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52),c("wkday","datetime","weeknum")]
summary(FORtabling$weeknum)
FORtabling$Date <- as.Date(FORtabling$datetime) #,'America/Los_Angeles'
summary(FORtabling$Date)
tabling <- FORtabling[,c("wkday","Date")]
tabling$wkday <- factor(tabling$wkday, levels=factorlevels)
#table(tabling)
weekdANOVA <- as.data.frame(table(tabling))
weekdANOVA$Date <- as.POSIXct(weekdANOVA$Date)
weekdANOVA <- weekdANOVA[which(weekdays(weekdANOVA$Date) == weekdANOVA$wkday),] #due to how table works, need to only keep counts for actual dat-weekday matches
weekdANOVA$Year <- year(weekdANOVA$Date)

print(ggplot() + 
    geom_boxplot(data=weekdANOVA, aes(x=wkday, y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
    geom_jitter(data=weekdANOVA, aes(x=wkday,y=Freq,color=factor(Year)), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
    #geom_point(data=weekdANOVA, aes(x=wkday, y=Freq, color=factor(Year)), alpha=1, size=3) +
    geom_hline(yintercept = mean(weekdANOVA$Freq,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weekdANOVA$Freq,na.rm=T)+1.96*sd(weekdANOVA$Freq,na.rm=T),
                              mean(weekdANOVA$Freq,na.rm=T)-1.96*sd(weekdANOVA$Freq,na.rm=T)),
               linetype=3) + 
    ylim((mean(weekdANOVA$Freq,na.rm=T)-2*sd(weekdANOVA$Freq,na.rm=T)),(mean(weekdANOVA$Freq,na.rm=T)+2*sd(weekdANOVA$Freq,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure counts") +
    ggtitle("Weekly seizure counts, aggregated by day of the week") + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png(paste("Weekday seizure counts, aggregated by day of the week, from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    geom_boxplot(data=weekdANOVA, aes(x=wkday, y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
    geom_jitter(data=weekdANOVA, aes(x=wkday,y=Freq,color=factor(Year)), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
    #geom_point(data=weekdANOVA, aes(x=wkday, y=Freq, color=factor(Year)), alpha=1, size=3) +
    geom_hline(yintercept = mean(weekdANOVA$Freq,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weekdANOVA$Freq,na.rm=T)+1.96*sd(weekdANOVA$Freq,na.rm=T),
                              mean(weekdANOVA$Freq,na.rm=T)-1.96*sd(weekdANOVA$Freq,na.rm=T)),
               linetype=3) + 
    ylim((mean(weekdANOVA$Freq,na.rm=T)-2*sd(weekdANOVA$Freq,na.rm=T)),(mean(weekdANOVA$Freq,na.rm=T)+2*sd(weekdANOVA$Freq,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure counts") +
    ggtitle("Weekly seizure counts, aggregated by day of the week") + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
attach(weekdANOVA)
Anova(lm(Freq ~ wkday,
         data=weekdANOVA),
      type="III")
day2countWEEK <- aov(lm(Freq ~ wkday))
day2countWEEK
posthoc <- TukeyHSD(x=day2countWEEK, 'wkday', conf.level = 0.95)
posthoc
hsdday2countWEEK <- HSD.test(day2countWEEK, "wkday")
hsdday2countWEEK
```
Doesn't look like there is a trend in aggregate...  

#It's worthwhile to attempt standardization by approximate incidence (through gross estimates of at-risk population)  
```{r pseudostandardized incidence rates per day}
#This will add in the relevant data incidence data, based on an approximation of unique, at-risk individuals
# -note this denominator of person-time is inaccurate for multiple reasons:
#  +it counts people "at risk" only if they've documented a seizure - i.e. ascertainment bias for those reporting
#  +it doesn't account for single documenters that then stop using the app - also an ascertainment bias
#  +it doesn't account for interventions (i.e. surgery, changes in regimen), assuming similar risk over similar time periods
#  +it doesn't account for "voyeurs" - people who signed up, but haven't documented yet

###=====This one takes a little while to run=====###
for(j in 1:nrow(weekdANOVA)) {
    denomdf <- Sz08to16[which(Sz08to16$datetime <= as.Date(weekdANOVA[j,"Date"])),"Unlinked_ID"]
    weekdANOVA[j,"AtRisk"] <- length(unique(denomdf))
    weekdANOVA[j,"Incidence"] <- weekdANOVA[j,"Freq"]/length(unique(denomdf))
}
###=====This one takes a little while to run=====###

p <- ggplot() 
for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    p <- p + geom_boxplot(data=weekdANOVA[which(weekdANOVA[,"Year"] == i),],
                 aes(x=wkday, y=Incidence),
                 fill=brewer.pal(n=(max(year(Sz08to16$datetime))-min(year(Sz08to16$datetime))),"Paired")[i-2007],
                 alpha=0.2,
                 outlier.size=-1, #Avoid duplicate outlier plotting
                 notch = T, #Enhance visibility
                 na.rm=T)
    p <- p + geom_jitter(data=weekdANOVA[which(weekdANOVA[,"Year"] == i),],
                aes(x=wkday,y=Incidence),
                color=brewer.pal(n=(max(year(Sz08to16$datetime))-min(year(Sz08to16$datetime))),"Paired")[i-2007],
                position=position_jitter(width=0.05),
                alpha=0.8,
                na.rm=T)#Outliers from incomplete weeks
}
p <- p + 
    ylim((mean(weekdANOVA$Incidence,na.rm=T)-2*sd(weekdANOVA$Incidence,na.rm=T)),(mean(weekdANOVA$Incidence,na.rm=T)+2*sd(weekdANOVA$Incidence,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure incidence rates (seizures per persons at risk)") +
    ggtitle("Weekly seizure incidence trends, by day of the week, separated by year") + 
    theme_bw()
p
print(p)

#That was a little messy, but it looks like the yearly pattern may be there, so plot them (and do ANOVA) separately
groups <- data.frame("Weekday"=weekendlist)
colid <- 2
for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    print(paste("Weekday seizure incidence trends for the 2nd through 51st [full] weeks, for the year of",i))
    wXyANOVA <- weekdANOVA[which(weekdANOVA$Year == i),]
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=Incidence), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=Incidence), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$Incidence,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$Incidence,na.rm=T)+1.96*sd(wXyANOVA$Incidence,na.rm=T),
                                  mean(wXyANOVA$Incidence,na.rm=T)-1.96*sd(wXyANOVA$Incidence,na.rm=T)),
                   linetype=3) + 
        ylim((mean(wXyANOVA$Incidence,na.rm=T)-2*sd(wXyANOVA$Incidence,na.rm=T)),(mean(wXyANOVA$Incidence,na.rm=T)+2*sd(wXyANOVA$Incidence,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure incidence rates (seizures per persons at risk)") +
        ggtitle(paste("Weekly seizure incidence trends, by day of the week for",i)) + 
        theme_bw())
    png(paste("Weekday seizure incidence trends for the 2nd through 51st (full) weeks, for the year of ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=Incidence), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=Incidence), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$Incidence,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$Incidence,na.rm=T)+1.96*sd(wXyANOVA$Incidence,na.rm=T),
                                  mean(wXyANOVA$Incidence,na.rm=T)-1.96*sd(wXyANOVA$Incidence,na.rm=T)),
                   linetype=3) + 
        ylim((mean(wXyANOVA$Incidence,na.rm=T)-2*sd(wXyANOVA$Incidence,na.rm=T)),(mean(wXyANOVA$Incidence,na.rm=T)+2*sd(wXyANOVA$Incidence,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure incidence rates (seizures per persons at risk)") +
        ggtitle(paste("Weekly seizure incidence trends, by day of the week for",i)) + 
        theme_bw())
    dev.off()
    attach(wXyANOVA)
    Anova(lm(Incidence ~ wkday,
             data=wXyANOVA),
          type="III")
    day2countWEEK <- aov(lm(Incidence ~ wkday))
    print(day2countWEEK)
    posthoc <- TukeyHSD(x=day2countWEEK, 'wkday', conf.level = 0.95)
    print(posthoc)
    hsdday2countWEEK <- HSD.test(day2countWEEK, "wkday")
    print(hsdday2countWEEK)
    plot(hsdday2countWEEK)
    png(paste("Honestly significant difference in seizure incidence, by weekday, for ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    plot(hsdday2countWEEK)
    dev.off()
    groups <- merge(groups,hsdday2countWEEK$groups[2],by.x="Weekday",by.y=0,sort=F)
    names(groups)[colid] <- i
    colid <- colid+1
}
print(groups)
```
  
#But the high variance introduced by recruitment may dilute the variation when comparing more stable at-risk population counts (i.e. over a given year)  
```{r parse out by year}
p <- ggplot() 
for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    p <- p + geom_boxplot(data=weekdANOVA[which(weekdANOVA[,"Year"] == i),],
                 aes(x=wkday, y=Freq),
                 fill=brewer.pal(n=(max(year(Sz08to16$datetime))-min(year(Sz08to16$datetime))),"Paired")[i-2007],
                 alpha=0.2,
                 outlier.size=-1, #Avoid duplicate outlier plotting
                 notch = T, #Enhance visibility
                 na.rm=T)
    p <- p + geom_jitter(data=weekdANOVA[which(weekdANOVA[,"Year"] == i),],
                aes(x=wkday,y=Freq),
                color=brewer.pal(n=(max(year(Sz08to16$datetime))-min(year(Sz08to16$datetime))),"Paired")[i-2007],
                position=position_jitter(width=0.05),
                alpha=0.8,
                na.rm=T)#Outliers from incomplete weeks
}
p <- p + 
    ylim((mean(weekdANOVA$Freq,na.rm=T)-2*sd(weekdANOVA$Freq,na.rm=T)),(mean(weekdANOVA$Freq,na.rm=T)+2*sd(weekdANOVA$Freq,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure counts") +
    ggtitle("Weekly seizure counts, aggregated by day of the week, separated by year") + 
    theme_bw()
p
print(p)

#That was a little messy, but it looks like the yearly pattern may be there, so plot them (and do ANOVA) separately

groups <- data.frame("Weekday"=weekendlist)
pvals <- data.frame("comparisons"=c("Thursday-Wednesday","Friday-Wednesday",",Saturday-Wednesday","Sunday-Wednesday","Monday-Wednesday","Tuesday-Wednesday","Friday-Thursday","Saturday-Thursday","Sunday-Thursday","Monday-Thursday","Tuesday-Thursday","Saturday-Friday","Sunday-Friday","Monday-Friday","Tuesday-Friday","Sunday-Saturday","Monday-Saturday","Tuesday-Saturday","Monday-Sunday","Tuesday-Sunday","Tuesday-Monday","ANOVA"),stringsAsFactors = F)
colid <- 2
for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    print(paste("Weekday seizure counts for the 2nd through 51st [full] weeks, for the year of",i))
    wXyANOVA <- weekdANOVA[which(weekdANOVA$Year == i),]
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=Freq), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$Freq,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$Freq,na.rm=T)+1.96*sd(wXyANOVA$Freq,na.rm=T),
                                  mean(wXyANOVA$Freq,na.rm=T)-1.96*sd(wXyANOVA$Freq,na.rm=T)),
                   linetype=3) + 
        ylim((mean(wXyANOVA$Freq,na.rm=T)-2*sd(wXyANOVA$Freq,na.rm=T)),(mean(wXyANOVA$Freq,na.rm=T)+2*sd(wXyANOVA$Freq,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure counts") +
        ggtitle(paste("Weekly seizure counts, aggregated by day of the week for",i)) + 
        theme_bw())
    png(paste("Weekday seizure counts for the 2nd through 51st (full) weeks, for the year of ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=Freq), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$Freq,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$Freq,na.rm=T)+1.96*sd(wXyANOVA$Freq,na.rm=T),
                                  mean(wXyANOVA$Freq,na.rm=T)-1.96*sd(wXyANOVA$Freq,na.rm=T)),
                   linetype=3) + 
        ylim((mean(wXyANOVA$Freq,na.rm=T)-2*sd(wXyANOVA$Freq,na.rm=T)),(mean(wXyANOVA$Freq,na.rm=T)+2*sd(wXyANOVA$Freq,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure counts") +
        ggtitle(paste("Weekly seizure counts, aggregated by day of the week for",i)) + 
        theme_bw())
    dev.off()
    attach(wXyANOVA)
    PANOVA <- Anova(lm(Freq ~ wkday,
                    data=wXyANOVA),
                    type="III")
    print(PANOVA)
    day2countWEEK <- aov(lm(Freq ~ wkday))
    print(day2countWEEK)
    posthoc <- TukeyHSD(x=day2countWEEK, 'wkday', conf.level = 0.95)
    print(posthoc)
    hsdday2countWEEK <- HSD.test(day2countWEEK, "wkday")
    print(hsdday2countWEEK)
    plot(hsdday2countWEEK)
    png(paste("Honestly significant difference in seizure counts, by weekday, for ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    plot(hsdday2countWEEK)
    dev.off()
    groups <- merge(groups,hsdday2countWEEK$groups[2],by.x="Weekday",by.y=0,sort=F)
    names(groups)[colid] <- i
    forPval <- data.frame("comparisons"=rownames(posthoc$wkday),
                          "year"=as.numeric(posthoc$wkday[,4]),
                          stringsAsFactors = F)
    forPval[nrow(forPval)+1,"comparisons"] <- "ANOVA"
    forPval[nrow(forPval),"year"] <- as.numeric(PANOVA$`Pr(>F)`[2])
    #rbind(forPval,data.frame("comparisons"="ANOVA",
    #                         "year"=as.numeric(PANOVA$`Pr(>F)`[2]),
    #                         stringsAsFactors = F))
    colnames(forPval)[2] <-i
    
    pvals <- merge.data.frame(pvals,
                              forPval,
                              by = intersect(names(pvals), names(forPval)),
                              sort = F)
    colid <- colid+1
}
print(groups)
print(pvals)
write.table(groups,"Tukey_groupings.txt",quote = F,row.names = F)
write.table(pvals,"ANOVA&Tukey_pvals.txt",quote = F,row.names = F)
###TO DO: do the above with scaled incidences
```
It's possible that there is a grouping effect for the weekends...  
  
#Now to look at it from the scaled incidences per weekday  
```{r scaled daily incidence multi-dien trends}
summary(Sz08to16$weeknum)
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
FORtabling <- Sz08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52),c("wkday","datetime","weeknum","scldIncidenceperDAY")]
summary(FORtabling$weeknum)
FORtabling$Date <- as.Date(FORtabling$datetime) #,'America/Los_Angeles'
summary(FORtabling$Date)
tabling <- FORtabling[,c("wkday","Date","scldIncidenceperDAY")]
tabling <- unique(tabling)
tabling$wkday <- factor(tabling$wkday, levels=factorlevels)
weekdANOVA <- tabling
weekdANOVA$Date <- as.POSIXct(weekdANOVA$Date)
weekdANOVA$Year <- year(weekdANOVA$Date)

print(ggplot() + 
    geom_boxplot(data=weekdANOVA, aes(x=wkday, y=scldIncidenceperDAY), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
    geom_jitter(data=weekdANOVA, aes(x=wkday,y=scldIncidenceperDAY,color=factor(Year)), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
    #geom_point(data=weekdANOVA, aes(x=wkday, y=scldIncidenceperDAY, color=factor(Year)), alpha=1, size=3) +
    #geom_hline(yintercept = mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)) + 
    #geom_hline(yintercept = c(mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)+1.96*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T),mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)-1.96*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T)),linetype=3) + 
    ylim(0,(mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)+2*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure incidence rates") +
    ggtitle("Weekly seizure incidence rates (scaled per individual), aggregated by day of the week") + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png(paste("Weekday seizure incidence rates, aggregated by day of the week, from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    geom_boxplot(data=weekdANOVA, aes(x=wkday, y=scldIncidenceperDAY), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
    geom_jitter(data=weekdANOVA, aes(x=wkday,y=scldIncidenceperDAY,color=factor(Year)), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
    #geom_point(data=weekdANOVA, aes(x=wkday, y=scldIncidenceperDAY, color=factor(Year)), alpha=1, size=3) +
    #geom_hline(yintercept = mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)) + 
    #geom_hline(yintercept = c(mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)+1.96*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T),mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)-1.96*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T)),linetype=3) + 
    ylim(0,(mean(weekdANOVA$scldIncidenceperDAY,na.rm=T)+2*sd(weekdANOVA$scldIncidenceperDAY,na.rm=T))) + 
    xlab("Weekday") +
    ylab("Weekly seizure incidence rates") +
    ggtitle("Weekly seizure incidence rates (scaled per individual), aggregated by day of the week") + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
attach(weekdANOVA)
Anova(lm(scldIncidenceperDAY ~ wkday,
         data=weekdANOVA),
      type="III")
day2countWEEK <- aov(lm(scldIncidenceperDAY ~ wkday))
day2countWEEK
posthoc <- TukeyHSD(x=day2countWEEK, 'wkday', conf.level = 0.95)
posthoc
hsdday2countWEEK <- HSD.test(day2countWEEK, "wkday")
hsdday2countWEEK

groups <- data.frame("Weekday"=weekendlist)
pvals <- data.frame("comparisons"=c("Thursday-Wednesday","Friday-Wednesday",",Saturday-Wednesday","Sunday-Wednesday","Monday-Wednesday","Tuesday-Wednesday","Friday-Thursday","Saturday-Thursday","Sunday-Thursday","Monday-Thursday","Tuesday-Thursday","Saturday-Friday","Sunday-Friday","Monday-Friday","Tuesday-Friday","Sunday-Saturday","Monday-Saturday","Tuesday-Saturday","Monday-Sunday","Tuesday-Sunday","Tuesday-Monday","ANOVA"),stringsAsFactors = F)
colid <- 2
for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
    print(paste("Weekday seizure incidence rates for the 2nd through 51st [full] weeks, for the year of",i))
    wXyANOVA <- weekdANOVA[which(weekdANOVA$Year == i),]
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=scldIncidenceperDAY), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=scldIncidenceperDAY), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)+1.96*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T),
                                  mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)-1.96*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T)),
                   linetype=3) + 
        ylim(0,(mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)+2*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure incidence rates") +
        ggtitle(paste("Weekly seizure incidence rates, aggregated by day of the week for",i)) + 
        theme_bw())
    
    png(paste("Weekday seizure incidence rates for the 2nd through 51st (full) weeks, for the year of ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot() + 
        geom_boxplot(data=wXyANOVA, aes(x=wkday, y=scldIncidenceperDAY), fill="#4271AE", alpha=0.5, outlier.size=-1,na.rm=T) + #Avoid duplicate outlier plotting
        geom_jitter(data=wXyANOVA, aes(x=wkday,y=scldIncidenceperDAY), position=position_jitter(width=0.05), alpha=0.8,na.rm=T) + #Outliers from incomplete weeks
        geom_hline(yintercept = mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)) + 
        geom_hline(yintercept = c(mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)+1.96*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T),
                                  mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)-1.96*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T)),
                   linetype=3) + 
        ylim(0,(mean(wXyANOVA$scldIncidenceperDAY,na.rm=T)+2*sd(wXyANOVA$scldIncidenceperDAY,na.rm=T))) + 
        xlab("Weekday") +
        ylab("Weekly seizure incidence rates") +
        ggtitle(paste("Weekly seizure incidence rates, aggregated by day of the week for",i)) + 
        theme_bw())
    dev.off()
    attach(wXyANOVA)
    PANOVA <- Anova(lm(scldIncidenceperDAY ~ wkday,
                    data=wXyANOVA),
                    type="III")
    print(PANOVA)
    day2countWEEK <- aov(lm(scldIncidenceperDAY ~ wkday))
    print(day2countWEEK)
    posthoc <- TukeyHSD(x=day2countWEEK, 'wkday', conf.level = 0.95)
    print(posthoc)
    hsdday2countWEEK <- HSD.test(day2countWEEK, "wkday")
    print(hsdday2countWEEK)
    plot(hsdday2countWEEK)
    png(paste("Honestly significant difference in seizure incidence rates, by weekday, for ",i,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    plot(hsdday2countWEEK)
    dev.off()
    groups <- merge(groups,hsdday2countWEEK$groups[2],by.x="Weekday",by.y=0,sort=F)
    names(groups)[colid] <- i
    forPval <- data.frame("comparisons"=rownames(posthoc$wkday),
                          "year"=as.numeric(posthoc$wkday[,4]),
                          stringsAsFactors = F)
    forPval[nrow(forPval)+1,"comparisons"] <- "ANOVA"
    forPval[nrow(forPval),"year"] <- as.numeric(PANOVA$`Pr(>F)`[2])
    #rbind(forPval,data.frame("comparisons"="ANOVA",
    #                         "year"=as.numeric(PANOVA$`Pr(>F)`[2]),
    #                         stringsAsFactors = F))
    colnames(forPval)[2] <-i
    
    pvals <- merge.data.frame(pvals,
                              forPval,
                              by = intersect(names(pvals), names(forPval)),
                              sort = F)
    colid <- colid+1
}
print(groups)
print(pvals)
write.table(groups,"Tukey_groupings_incidence.txt",quote = F,row.names = F)
write.table(pvals,"ANOVA&Tukey_pvals_incidence.txt",quote = F,row.names = F)
```
  

  
Seizure incidence rate ratios (approximated, as different denominators of person-time)  
```{r rate ratio trends}
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
trending <- Sz08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52),]
daytrend <- data.frame("Year"=year(trending$datetime),
                       "RelativeDay"=(yday(trending$datetime) - trending$DSTday),
                       "DailyIncidence"=trending$IncidenceperDAY,
                       "AtRisk"=trending$AtRiskperDAY)
#Calculate approximate "rate ratio" relative to DST
for(i in min(daytrend$Year):max(daytrend$Year)) {
    DSTinc <- mean(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),"DailyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),]))
    daytrend[which(daytrend$Year == i),"RateRatio"] <- daytrend[which(daytrend$Year == i),"DailyIncidence"]/DSTinc
}

#Because each representation at a given day of the year contains the same incidence for that day, need to remove duplicates before removing outliers (can verify by checking dim of daytrend after outlier removal if unique is done before or after the outlier removal)
daytrend <- unique(daytrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
daytrend <- daytrend[which(daytrend$RateRatio > quantile(daytrend$RateRatio, 0.01, na.rm=T)[[1]] & daytrend$RateRatio < quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]),]
daystats <- data.frame("RelativeDay"=numeric(),
                       "Mean"=numeric(),
                       "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
#    daystats[index,"RelativeDay"] <- i
#    daystats[index,"Mean"] <- mean(daytrend[which(daytrend$RelativeDay == i),"RateRatio"])
#    daystats[index,"SD"] <- sd(daytrend[which(daytrend$RelativeDay == i),"RateRatio"])
#    index=index+1
#}

index=1
for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
    daystats[index,"RelativeDay"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(daytrend[which(daytrend$RelativeDay == i),"RateRatio"], daytrend[which(daytrend$RelativeDay == i),"AtRisk"])
    daystats[index,"Mean"] <- WA
    WSD <- sqrt(sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"] * (daytrend[which(daytrend$RelativeDay == i),"RateRatio"] - WA)^2)/sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"]))
    daystats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Daily rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=unique(daytrend),
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(data=unique(daytrend),
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=0.1,
                se=FALSE) + 
    geom_smooth(data=unique(daytrend),
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Daily rate ratios with loess averaging of trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=unique(daytrend),
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(data=unique(daytrend),
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=0.1,
                se=FALSE) + 
    geom_smooth(data=unique(daytrend),
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Daily rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

weektrend <- data.frame("Year"=year(trending$datetime),
                        "RelativeWeek"=(epiweek(trending$datetime) - trending$DSTweek),
                        "WeeklyIncidence"=trending$IncidenceperWEEK,
                        "AtRisk"=trending$AtRiskperWEEK)
#Calculate approximate "rate ratio" relative to DST
for(i in min(weektrend$Year):max(weektrend$Year)) {
    DSTinc <- mean(weektrend[which(weektrend$RelativeWeek == 0 & weektrend$Year == i),"WeeklyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(weektrend[which(weektrend$RelativeWeek == 0 & weektrend$Year == i),]))
    weektrend[which(weektrend$Year == i),"RateRatio"] <- weektrend[which(weektrend$Year == i),"WeeklyIncidence"]/DSTinc
}
#Removing duplicate entries (should be the case for each week to have n duplicates, where n is the number of seizures that contributed to the incidence in that time period)...important to remove before outlier removal as different Ns per week will cause biased outlier removal
weektrend <- unique(weektrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
weektrend <- weektrend[which(weektrend$RateRatio > quantile(weektrend$RateRatio, 0.01, na.rm=T)[[1]] & weektrend$RateRatio < quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]),]
weekstats <- data.frame("RelativeWeek"=numeric(),
                        "Mean"=numeric(),
                        "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
#    weekstats[index,"RelativeWeek"] <- i
#    weekstats[index,"Mean"] <- mean(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"])
#    weekstats[index,"SD"] <- sd(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"])#/nrow(weektrend[which(weektrend$RelativeWeek == i),])
#    index=index+1
#}

index=1
for(i in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
    weekstats[index,"RelativeWeek"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"], weektrend[which(weektrend$RelativeWeek == i),"AtRisk"])
    weekstats[index,"Mean"] <- WA
    WSD <- sqrt(sum(weektrend[which(weektrend$RelativeWeek == i),"AtRisk"] * (weektrend[which(weektrend$RelativeWeek == i),"RateRatio"] - WA)^2)/sum(weektrend[which(weektrend$RelativeWeek == i),"AtRisk"]))
    weekstats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=weektrend, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weektrend, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weektrend, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weektrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weektrend$RateRatio,na.rm=T)+1.96*sd(weektrend$RateRatio,na.rm=T),
                              mean(weektrend$RateRatio,na.rm=T)-1.96*sd(weektrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Weekly rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=weektrend, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weektrend, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weektrend, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weektrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weektrend$RateRatio,na.rm=T)+1.96*sd(weektrend$RateRatio,na.rm=T),
                              mean(weektrend$RateRatio,na.rm=T)-1.96*sd(weektrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot(data=weektrend,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    #geom_point(alpha=0.3) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(se=FALSE, method="loess", span=0.3) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Weekly rate ratios with loess averaging and yearly trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(data=weektrend,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    #geom_point(alpha=0.3) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(se=FALSE, method="loess", span=0.3) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=weektrend, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Weekly rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=weektrend, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
```
  
Individual-seizure-propensity-adusted seizure incidence rate ratios (approximated, as different denominators of person-time)  
```{r rate ratio trends - adjusted for individual yearly seizure counts}
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
reltrend <- Sz08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52),]
daytrend <- data.frame("Year"=year(reltrend$datetime),
                       "RelativeDay"=(yday(reltrend$datetime) - reltrend$DSTday),
                       "DailyIncidence"=reltrend$relIncidenceperDAY,
                       "AtRisk"=reltrend$AtRiskperDAY)
dayagg <- data.frame("Year"=numeric(),
                     "RelativeDay"=numeric(),
                     "DailyIncidence"=numeric(),
                     "RateRatio"=numeric())

#Calculate approximate "rate ratio" relative to DST
index=1
for(i in min(daytrend$Year):max(daytrend$Year)) {
    DSTinc <- mean(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),"DailyIncidence"])
    daytrend[which(daytrend$Year == i),"RateRatio"] <- daytrend[which(daytrend$Year == i),"DailyIncidence"]/DSTinc
    #This loop is to integrate the individual-adjusted, per-person incidences into an aggregated incidence over the time period (1 day), separately for each year. Recall the individual-adjusted, per-person incidence is each individual's seizure, divided by their yearly seizure count, then divided by the person-time at risk, but in reality this is just divided by the number at risk in that time window (because the time frame will be the same and drop out when calculating the Rate Ratios). So, because each person has a different individually-adjusted incidence, an aggregate measure is made from the mean of the individual-adjusted incidences, for each time window (ie, 1 day), and then a Rate Ratio is calculated with respect to the individual-adjusted, DST incidence.
    for(j in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
        dayagg[index,"Year"] <- i
        dayagg[index,"RelativeDay"] <- j
        dayagg[index,"DailyIncidence"] <- mean(daytrend[which(daytrend$RelativeDay == j & daytrend$Year == i),"DailyIncidence"])
        dayagg[index,"RateRatio"] <- mean(daytrend[which(daytrend$RelativeDay == j & daytrend$Year == i),"DailyIncidence"])/DSTinc
        index <- index + 1
    }
}

#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
daytrend <- daytrend[which(daytrend$RateRatio > quantile(daytrend$RateRatio, 0.01, na.rm=T)[[1]] & daytrend$RateRatio < quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]),]
dayagg <- dayagg[which(dayagg$RateRatio > quantile(dayagg$RateRatio, 0.01, na.rm=T)[[1]] & dayagg$RateRatio < quantile(dayagg$RateRatio, 0.99, na.rm=T)[[1]]),]
forstats <- unique(daytrend[order( daytrend[,1], daytrend[,2] ),-c(3,5)]) #Removes DailyIncidence & Rate Ratio
forstats <- merge.data.frame(dayagg, forstats, na.last=NA)
forstats <- forstats[order( forstats[,1], forstats[,2] ),]
daystats <- data.frame("RelativeDay"=numeric(),
                       "Mean"=numeric(),
                       "SD"=numeric())
###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
#    daystats[index,"RelativeDay"] <- i
#    daystats[index,"Mean"] <- mean(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    daystats[index,"SD"] <- sd(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    index=index+1
#}

index=1
for(i in min(forstats$RelativeDay):max(forstats$RelativeDay)) {
    daystats[index,"RelativeDay"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(forstats[which(forstats$RelativeDay == i),"RateRatio"], forstats[which(forstats$RelativeDay == i),"AtRisk"])
    daystats[index,"Mean"] <- WA
    WSD <- sqrt(sum(forstats[which(forstats$RelativeDay == i),"AtRisk"] * (forstats[which(forstats$RelativeDay == i),"RateRatio"] - WA)^2)/sum(forstats[which(forstats$RelativeDay == i),"AtRisk"]))
    daystats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=dayagg, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=dayagg, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=dayagg, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(dayagg$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(dayagg$RateRatio,na.rm=T)+1.96*sd(dayagg$RateRatio,na.rm=T),
                              mean(dayagg$RateRatio,na.rm=T)-1.96*sd(dayagg$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Individual-adjusted Rate Ratio (Sz incidence vs DST)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0,quantile(dayagg$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted daily rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=dayagg, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=dayagg, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=dayagg, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(dayagg$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(dayagg$RateRatio,na.rm=T)+1.96*sd(dayagg$RateRatio,na.rm=T),
                              mean(dayagg$RateRatio,na.rm=T)-1.96*sd(dayagg$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Individual-adjusted Rate Ratio (Sz incidence vs DST)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0,quantile(dayagg$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    geom_point(data=unique(dayagg),
               aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
               alpha=0.25) + 
    #geom_smooth(method="loess", span=1/52, se=TRUE, alpha=0.3, colour="red") + 
    geom_smooth(data=unique(dayagg),
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=0.01,
                se=TRUE,
                alpha=0.5,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Individual-adjusted daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

print(ggplot(data=unique(dayagg), aes(x=RelativeDay,y=RateRatio,color=factor(Year))) + 
    #geom_point(data=unique(dayagg),
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    #geom_smooth(method="loess", span=1/52, se=TRUE, alpha=0.3, colour="red") + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(se=FALSE, method="loess", span=0.1, alpha=0.5) + 
    geom_smooth(method="loess",
                span=0.01,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Individual-adjusted daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted daily rate ratios with loess averaging of trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(data=unique(dayagg), aes(x=RelativeDay,y=RateRatio,color=factor(Year))) + 
    #geom_point(data=unique(dayagg),
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    #geom_smooth(method="loess", span=1/52, se=TRUE, alpha=0.3, colour="red") + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(se=FALSE, method="loess", span=0.1, alpha=0.5) + 
    geom_smooth(method="loess",
                span=0.01,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Individual-adjusted daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=dayagg, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Individual-adjusted daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted daily rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=dayagg, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Individual-adjusted daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-adjusted daily Rate Ratio trends over a year") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

weektrend <- data.frame("Year"=year(reltrend$datetime),
                        "RelativeWeek"=(epiweek(reltrend$datetime) - reltrend$DSTweek),
                        "WeeklyIncidence"=reltrend$relIncidenceperWEEK,
                        "AtRisk"=reltrend$AtRiskperWEEK)
weekagg <- data.frame("Year"=numeric(),
                      "RelativeWeek"=numeric(),
                      "WeeklyIncidence"=numeric(),
                      "RateRatio"=numeric())

#Calculate approximate "rate ratio" relative to DST
index=1
for(i in min(weektrend$Year):max(weektrend$Year)) {
    DSTinc <- mean(weektrend[which(weektrend$RelativeWeek == 0 & weektrend$Year == i),"WeeklyIncidence"])
    weektrend[which(weektrend$Year == i),"RateRatio"] <- weektrend[which(weektrend$Year == i),"WeeklyIncidence"]/DSTinc
    #This loop is to integrate the individual-adjusted, per-person incidences into an aggregated incidence over the time period (1 week), separately for each year. Recall the individual-adjusted, per-person incidence is each individual's seizure, divided by their yearly seizure count, then divided by the person-time at risk, but in reality this is just divided by the number at risk in that time window (because the time frame will be the same and drop out when calculating the Rate Ratios). So, because each person has a different individually-adjusted incidence, an aggregate measure is made from the mean of the individual-adjusted incidences, for each time window (ie, 1 week), and then a Rate Ratio is calculated with respect to the individual-adjusted, DST incidence.
    for(j in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
        weekagg[index,"Year"] <- i
        weekagg[index,"RelativeWeek"] <- j
        weekagg[index,"WeeklyIncidence"] <- mean(weektrend[which(weektrend$RelativeWeek == j & weektrend$Year == i),"WeeklyIncidence"])
        weekagg[index,"RateRatio"] <- mean(weektrend[which(weektrend$RelativeWeek == j & weektrend$Year == i),"WeeklyIncidence"])/DSTinc
        index <- index + 1
    }
}

#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
weektrend <- weektrend[which(weektrend$RateRatio > quantile(weektrend$RateRatio, 0.01, na.rm=T)[[1]] & weektrend$RateRatio < quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]),]
weekagg <- weekagg[which(weekagg$RateRatio > quantile(weekagg$RateRatio, 0.01, na.rm=T)[[1]] & weekagg$RateRatio < quantile(weekagg$RateRatio, 0.99, na.rm=T)[[1]]),]
forstats <- unique(weektrend[order( weektrend[,1], weektrend[,2] ),-c(3,5)]) #Removes WeeklyIncidence & Rate Ratio
forstats <- merge.data.frame(weekagg, forstats, na.last=NA)
forstats <- forstats[order( forstats[,1], forstats[,2] ),]
weekstats <- data.frame("RelativeWeek"=numeric(),
                        "Mean"=numeric(),
                        "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
#    weekstats[index,"RelativeWeek"] <- i
#    weekstats[index,"Mean"] <- mean(weekagg[which(weekagg$RelativeWeek == i),"RateRatio"])
#    weekstats[index,"SD"] <- sd(weekagg[which(weekagg$RelativeWeek == i),"RateRatio"])/nrow(weekagg[which(weekagg$RelativeWeek == i),])
#    index=index+1
#}

index=1
for(i in min(forstats$RelativeWeek):max(forstats$RelativeWeek)) {
    weekstats[index,"RelativeWeek"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(forstats[which(forstats$RelativeWeek == i),"RateRatio"], forstats[which(forstats$RelativeWeek == i),"AtRisk"])
    weekstats[index,"Mean"] <- WA
    WSD <- sqrt(sum(forstats[which(forstats$RelativeWeek == i),"AtRisk"] * (forstats[which(forstats$RelativeWeek == i),"RateRatio"] - WA)^2)/sum(forstats[which(forstats$RelativeWeek == i),"AtRisk"]))
    weekstats[index,"SD"] <- WSD
    index=index+1
}

#Removing duplicate entries (should be the case for each week to have n duplicates, where n is the number of seizures that contributed to the incidence in that time period)
weektrend <- unique(weektrend)
weekagg <- unique(weekagg)

print(ggplot() + 
    #geom_boxplot(data=weekagg, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weekagg, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weekagg, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weekagg$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weekagg$RateRatio,na.rm=T)+1.96*sd(weekagg$RateRatio,na.rm=T),
                              mean(weekagg$RateRatio,na.rm=T)-1.96*sd(weekagg$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition week, indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted weekly rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=weekagg, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weekagg, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weekagg, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weekagg$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weekagg$RateRatio,na.rm=T)+1.96*sd(weekagg$RateRatio,na.rm=T),
                              mean(weekagg$RateRatio,na.rm=T)-1.96*sd(weekagg$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition week, indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_point(data=weekagg,
               aes(x=RelativeWeek,y=RateRatio,color=factor(Year)), 
               alpha=0.5) + 
    #geom_smooth(method="loess", span=1/52, se=TRUE, alpha=0.3, colour="red") + 
    geom_smooth(data=weekagg,
                aes(x=RelativeWeek,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.5,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

print(ggplot(data=weekagg,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    #geom_point(alpha=0.3) + 
    geom_smooth(se=FALSE, method="loess", span=0.2) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted weekly rate ratios with loess averaging and yearly trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(data=weekagg,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    #geom_point(alpha=0.3) + 
    geom_smooth(se=FALSE, method="loess", span=0.2) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=weekagg, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-adjusted weekly rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=weekagg, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-adjusted weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
```
  
Individual-yearly-seizure-propensity-scaled seizure incidence rate ratios (approximated, as different denominators of person-time)  
```{r rate ratio trends - scaled for individual yearly seizure counts}
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
scldtrend <- Sz08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52),]
daytrend <- data.frame("Year"=year(scldtrend$datetime),
                       "RelativeDay"=(yday(scldtrend$datetime) - scldtrend$DSTday),
                       "DailyIncidence"=scldtrend$scldIncidenceperDAY,
                       "AtRisk"=reltrend$AtRiskperDAY)
#Calculate approximate "rate ratio" relative to DST
for(i in min(daytrend$Year):max(daytrend$Year)) {
    DSTinc <- mean(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),"DailyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),]))
    daytrend[which(daytrend$Year == i),"RateRatio"] <- daytrend[which(daytrend$Year == i),"DailyIncidence"]/DSTinc
}
#Because each representation at a given day of the year contains the same incidence for that day, need to remove duplicates before removing outliers (can verify by checking dim of daytrend after outlier removal if unique is done before or after the outlier removal)
###TO DO (do unique before stats for general and relative chunks above)...and DO WEIGHTED AVERAGES
daytrend <- unique(daytrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
daytrend <- daytrend[which(daytrend$RateRatio > quantile(daytrend$RateRatio, 0.01, na.rm=T)[[1]] & daytrend$RateRatio < quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]),]
daystats <- data.frame("RelativeDay"=numeric(),
                       "Mean"=numeric(),
                       "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
#    daystats[index,"RelativeDay"] <- i
#    daystats[index,"Mean"] <- mean(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    daystats[index,"SD"] <- sd(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    index=index+1
#}

index=1
for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
    daystats[index,"RelativeDay"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(daytrend[which(daytrend$RelativeDay == i),"RateRatio"], daytrend[which(daytrend$RelativeDay == i),"AtRisk"])
    daystats[index,"Mean"] <- WA
    WSD <- sqrt(sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"] * (daytrend[which(daytrend$RelativeDay == i),"RateRatio"] - WA)^2)/sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"]))
    daystats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled daily rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend,
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
                method="loess",
                span=0.1,
                se=FALSE) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled daily rate ratios with loess averaging of trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend,
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
                method="loess",
                span=0.1,
                se=FALSE) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled daily rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="black") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

weektrend <- data.frame("Year"=year(scldtrend$datetime),
                        "RelativeWeek"=(epiweek(scldtrend$datetime) - scldtrend$DSTweek),
                        "WeeklyIncidence"=scldtrend$scldIncidenceperWEEK,
                        "AtRisk"=reltrend$AtRiskperWEEK)
#Calculate approximate "rate ratio" relative to DST
for(i in min(weektrend$Year):max(weektrend$Year)) {
    DSTinc <- mean(weektrend[which(weektrend$RelativeWeek == 0 & weektrend$Year == i),"WeeklyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(weektrend[which(weektrend$RelativeWeek == 0 & weektrend$Year == i),]))
    weektrend[which(weektrend$Year == i),"RateRatio"] <- weektrend[which(weektrend$Year == i),"WeeklyIncidence"]/DSTinc
}
#Removing duplicate entries (should be the case for each week to have n duplicates, where n is the number of seizures that contributed to the incidence in that time period)...important to remove before outlier removal as different Ns per week will cause biased outlier removal
weektrend <- unique(weektrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
weektrend <- weektrend[which(weektrend$RateRatio > quantile(weektrend$RateRatio, 0.01, na.rm=T)[[1]] & weektrend$RateRatio < quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]),]
weekstats <- data.frame("RelativeWeek"=numeric(),
                        "Mean"=numeric(),
                        "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
#    weekstats[index,"RelativeWeek"] <- i
#    weekstats[index,"Mean"] <- mean(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"])
#    weekstats[index,"SD"] <- sd(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"])#/nrow(weektrend[which(weektrend$RelativeWeek == i),])
#    index=index+1
#}

index=1
for(i in min(weektrend$RelativeWeek):max(weektrend$RelativeWeek)) {
    weekstats[index,"RelativeWeek"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(weektrend[which(weektrend$RelativeWeek == i),"RateRatio"], weektrend[which(weektrend$RelativeWeek == i),"AtRisk"])
    weekstats[index,"Mean"] <- WA
    WSD <- sqrt(sum(weektrend[which(weektrend$RelativeWeek == i),"AtRisk"] * (weektrend[which(weektrend$RelativeWeek == i),"RateRatio"] - WA)^2)/sum(weektrend[which(weektrend$RelativeWeek == i),"AtRisk"]))
    weekstats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=weektrend, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weektrend, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weektrend, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weektrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weektrend$RateRatio,na.rm=T)+1.96*sd(weektrend$RateRatio,na.rm=T),
                              mean(weektrend$RateRatio,na.rm=T)-1.96*sd(weektrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled weekly rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=weektrend, aes(x=RelativeWeek, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=weektrend, aes(x=RelativeWeek, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=weektrend, aes(x=RelativeWeek, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(weektrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(weektrend$RateRatio,na.rm=T)+1.96*sd(weektrend$RateRatio,na.rm=T),
                              mean(weektrend$RateRatio,na.rm=T)-1.96*sd(weektrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Week of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    geom_point(data=weektrend,
               aes(x=RelativeWeek,y=RateRatio,color=factor(Year)), 
               alpha=0.5) + 
    #geom_smooth(method="loess", span=1/52, se=TRUE, alpha=0.3, colour="red") + 
    geom_smooth(data=weektrend,
                aes(x=RelativeWeek,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.5,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

print(ggplot(data=weektrend,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    #geom_point(alpha=0.3) + 
    geom_smooth(se=FALSE, method="loess", span=0.3) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled weekly rate ratios with loess averaging and yearly trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(data=weektrend,
       aes(x=RelativeWeek,y=RateRatio,color=factor(Year))) + 
    #geom_point(alpha=0.3) + 
    geom_smooth(se=FALSE, method="loess", span=0.3) + 
    geom_smooth(method="loess",
                span=0.1,
                se=TRUE,
                alpha=0.75,
                colour="black") + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(weektrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=weektrend, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled weekly rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=weektrend, aes(x=RelativeWeek,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=weekstats, aes(x=RelativeWeek,y=Mean),size=1,color="black") + 
    geom_ribbon(data=weekstats,aes(x=RelativeWeek,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5) + 
    geom_vline(xintercept=c(0,1,33,34)) + 
    annotate("rect", xmin=0, xmax=1, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=33, xmax=34, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Week of the year (indexed to DST transition)") +
    ylab("Weekly Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled weekly Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
```
  
Diurnal vs nocturnal individual-yearly-seizure-propensity-scaled seizure incidence rate ratios (approximated, as different denominators of person-time)  
```{r Diem vs Nocturnum rate ratio trends - scaled for individual yearly seizure counts}
#Because first (1st) and last weeks (52nd or 53rd) can be partial weeks, will remove so as not to bias averages for given weekdays
diemtrend <- Day08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52 & Sz08to16$overnight == 0),]
nocttrend <- Night08to16[which(Sz08to16$weeknum > 1 & Sz08to16$weeknum < 52 & Sz08to16$overnight == 1),]
daytrend <- data.frame("Year"=year(diemtrend$datetime),
                       "RelativeDay"=(yday(diemtrend$datetime) - diemtrend$DSTday),
                       "DailyIncidence"=diemtrend$scldIncidenceperDAY,
                       "AtRisk"=diemtrend$AtRiskperDAY)
daytrend <- na.omit(daytrend)
nighttrend <- data.frame("Year"=year(nocttrend$datetime),
                         "RelativeDay"=(yday(nocttrend$datetime) - nocttrend$DSTday),
                         "DailyIncidence"=nocttrend$scldIncidenceperDAY,
                         "AtRisk"=nocttrend$AtRiskperDAY)
nighttrend <- na.omit(nighttrend)
#Calculate approximate "rate ratio" relative to DST
for(i in min(daytrend$Year):max(daytrend$Year)) {
    DSTinc <- mean(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),"DailyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(daytrend[which(daytrend$RelativeDay == 0 & daytrend$Year == i),]))
    daytrend[which(daytrend$Year == i),"RateRatio"] <- daytrend[which(daytrend$Year == i),"DailyIncidence"]/DSTinc
}
for(i in min(nighttrend$Year):max(nighttrend$Year)) {
    DSTinc <- mean(nighttrend[which(nighttrend$RelativeDay == 0 & nighttrend$Year == i),"DailyIncidence"])
    #Even though getting mean DST incidence, it can be verified that it's the same for any year: 
    print(summary(nighttrend[which(nighttrend$RelativeDay == 0 & nighttrend$Year == i),]))
    nighttrend[which(nighttrend$Year == i),"RateRatio"] <- nighttrend[which(nighttrend$Year == i),"DailyIncidence"]/DSTinc
}
#Because each representation at a given day of the year contains the same incidence for that day, need to remove duplicates before removing outliers (can verify by checking dim of daytrend after outlier removal if unique is done before or after the outlier removal)
daytrend <- unique(daytrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
daytrend <- daytrend[which(daytrend$RateRatio > quantile(daytrend$RateRatio, 0.01, na.rm=T)[[1]] & daytrend$RateRatio < quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]),]
daystats <- data.frame("RelativeDay"=numeric(),
                       "Mean"=numeric(),
                       "SD"=numeric())
nighttrend <- unique(nighttrend)
#Eliminate spuriously extreme outliers (beyond 1st/99th percentiles)
nighttrend <- nighttrend[which(nighttrend$RateRatio > quantile(nighttrend$RateRatio, 0.01, na.rm=T)[[1]] & nighttrend$RateRatio < quantile(nighttrend$RateRatio, 0.99, na.rm=T)[[1]]),]
nightstats <- data.frame("RelativeDay"=numeric(),
                         "Mean"=numeric(),
                         "SD"=numeric())

###PREVIOUS METHOD without weighted averages and SDs
#index=1
#for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
#    daystats[index,"RelativeDay"] <- i
#    daystats[index,"Mean"] <- mean(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    daystats[index,"SD"] <- sd(dayagg[which(dayagg$RelativeDay == i),"RateRatio"])
#    index=index+1
#}

index=1
for(i in min(daytrend$RelativeDay):max(daytrend$RelativeDay)) {
    daystats[index,"RelativeDay"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(daytrend[which(daytrend$RelativeDay == i),"RateRatio"], daytrend[which(daytrend$RelativeDay == i),"AtRisk"])
    daystats[index,"Mean"] <- WA
    WSD <- sqrt(sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"] * (daytrend[which(daytrend$RelativeDay == i),"RateRatio"] - WA)^2)/sum(daytrend[which(daytrend$RelativeDay == i),"AtRisk"]))
    daystats[index,"SD"] <- WSD
    index=index+1
}
index=1
for(i in min(nighttrend$RelativeDay):max(nighttrend$RelativeDay)) {
    nightstats[index,"RelativeDay"] <- i
    #Creating a weighted average and weighted SD
    WA <- weighted.mean(nighttrend[which(nighttrend$RelativeDay == i),"RateRatio"], nighttrend[which(nighttrend$RelativeDay == i),"AtRisk"])
    nightstats[index,"Mean"] <- WA
    WSD <- sqrt(sum(nighttrend[which(nighttrend$RelativeDay == i),"AtRisk"] * (nighttrend[which(nighttrend$RelativeDay == i),"RateRatio"] - WA)^2)/sum(nighttrend[which(nighttrend$RelativeDay == i),"AtRisk"]))
    nightstats[index,"SD"] <- WSD
    index=index+1
}

print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled daily rate ratios (relative to DST).png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_boxplot(data=daytrend, aes(x=RelativeDay, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
    #geom_point(data=daytrend, aes(x=RelativeDay, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
    geom_line() + 
    stat_summary(data=daytrend, aes(x=RelativeDay, y=RateRatio, group=Year, color=factor(Year)), geom="line", fun.y=mean) + 
    geom_hline(yintercept = mean(daytrend$RateRatio,na.rm=T)) + 
    geom_hline(yintercept = c(mean(daytrend$RateRatio,na.rm=T)+1.96*sd(daytrend$RateRatio,na.rm=T),
                              mean(daytrend$RateRatio,na.rm=T)-1.96*sd(daytrend$RateRatio,na.rm=T)),
               linetype=3) + 
    xlab("Day of year (relative to DST transition on Sunday - indexed as 0)") +
    ylab("Rate Ratio (Sz incidence compared to DST)") +
    ggtitle("Individual-scaled daily Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0,quantile(daytrend$RateRatio, 0.99, na.rm=T)[[1]]) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend,
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    #geom_smooth(data=daytrend,
    #            aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
    #            method="loess",
    #            span=0.1,
    #            se=FALSE) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="orange4",
                fill="orange1") + 
    #geom_smooth(data=nighttrend,
    #            aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
    #            method="loess",
    #            span=0.1,
    #            se=FALSE) + 
    geom_smooth(data=nighttrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="blue4",
                fill="blue1") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled day and night Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled day and night rate ratios with loess averaging of trends.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend,
    #           aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
    #           alpha=0.25) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    #geom_smooth(data=daytrend,
    #            aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
    #            method="loess",
    #            span=0.1,
    #            se=FALSE) + 
    geom_smooth(data=daytrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="orange4",
                fill="orange1") + 
    #geom_smooth(data=nighttrend,
    #            aes(x=RelativeDay,y=RateRatio,color=factor(Year)),
    #            method="loess",
    #            span=0.1,
    #            se=FALSE) + 
    geom_smooth(data=nighttrend,
                aes(x=RelativeDay,y=RateRatio,color=factor(Year)), 
                method="loess",
                span=7/365,
                se=TRUE,
                alpha=0.5,
                colour="blue4",
                fill="blue1") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SEM)") +
    ggtitle("Individual-scaled day and night Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="orange1") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="orange1") + 
    geom_line(data=nightstats, aes(x=RelativeDay,y=Mean),size=1,color="blue4") + 
    geom_ribbon(data=nightstats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="blue4") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled day and night Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled day and night rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="orange1") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="orange1") + 
    geom_line(data=nightstats, aes(x=RelativeDay,y=Mean),size=1,color="blue4") + 
    geom_ribbon(data=nightstats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="blue4") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled day and night Rate Ratio trends over a year, indexed to DST") + 
    #ylim(0.5,2) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="orange1") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="orange1") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled daytime Rate Ratio trends over a year, indexed to DST") + 
    ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled daytime rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=daystats, aes(x=RelativeDay,y=Mean),size=1,color="orange1") + 
    geom_ribbon(data=daystats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="orange1") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled daytime Rate Ratio trends over a year, indexed to DST") + 
    ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()

print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=nightstats, aes(x=RelativeDay,y=Mean),size=1,color="blue4") + 
    geom_ribbon(data=nightstats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="blue4") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled nighttime Rate Ratio trends over a year, indexed to DST") + 
    ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))

png("Individual-scaled nighttime rate ratio trends over a year, indexed to DST.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot() + 
    #geom_point(data=daytrend, aes(x=RelativeDay,y=RateRatio,color=Year), alpha=0.01) + 
    geom_hline(yintercept = 1, linetype = 3) + 
    geom_line(data=nightstats, aes(x=RelativeDay,y=Mean),size=1,color="blue4") + 
    geom_ribbon(data=nightstats,aes(x=RelativeDay,ymin=(Mean+SD),ymax=(Mean-SD)),alpha=0.5,fill="blue4") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Daily Rate Ratio trends over a year (mean \u00b1SD)") +
    ggtitle("Individual-scaled nighttime Rate Ratio trends over a year, indexed to DST") + 
    ylim(0.5,2.25) + 
    theme_bw() + 
    theme(legend.title = element_blank()))
dev.off()
```
  
Seizure count comparisons by weekday  
```{r a function for comparing weekdays, defaulted comparison between DST and all non-DST}
compareweekdays <- function(firstweek=Sz08to16wkofDST,
                            secondweek=Sz08to16notDST,
                            wkone="week of DST",
                            wktwo="all non DST") {
    
    list <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
    week2weekstats <- data.frame("Weekday"=character(),
                                 "DSTmean"=numeric(),
                                 "DSTsd"=numeric(),
                                 "COMPmean"=numeric(),
                                 "COMPsd"=numeric(),
                                 "FreqP"=numeric(),
                                 "FreqT"=numeric(),
                                 "Freqdf"=numeric(),
                                 "Freqd"=numeric(),
                                 "RateRatio"=numeric(),
                                 "lCI"=numeric(),
                                 "uCI"=numeric(),
                                 "RRP"=numeric(),
                                 "RRT"=numeric(),
                                 "RRdf"=numeric(),
                                 "RRd"=numeric(),
                                 stringsAsFactors = F)
    
    #Get firstweek's scaled data
    firstscld <- firstweek[,c("datetime","AtRiskperDAY","scldIncidenceperDAY")]
    firstscld$datetime <- as.Date(firstscld$datetime,'America/Los_Angeles')
    firstscld <- unique(firstscld)
    names(firstscld)[1] <- "Var1"
    duplicated(firstscld) #no duplicated entries (confirms the AtRisk and scldIncidence values are correct)
    
    #Get secondweek's scaled data
    secondscld <- secondweek[,c("datetime","AtRiskperDAY","scldIncidenceperDAY")]
    secondscld$datetime <- as.Date(secondscld$datetime,'America/Los_Angeles')
    secondscld <- unique(secondscld)
    names(secondscld)[1] <- "Var1"
    duplicated(secondscld) #no duplicated entries (confirms the AtRisk and scldIncidence values are correct)
    
    week2week <- data.frame("Weekday"=character(),
                            "Year"=numeric(),
                            "RateRatio"=numeric(),
                            stringsAsFactors = F)
    
    firstdf <- data.frame("Week"=character(),
                          "Weekday"=character(),
                          "Mean_Sz_count"=numeric(),
                          "sd"=numeric(),
                          "se"=numeric(),
                          stringsAsFactors = F)
    seconddf <- data.frame("Week"=character(),
                           "Weekday"=character(),
                           "Mean_Sz_count"=numeric(),
                           "sd"=numeric(),
                           "se"=numeric(),
                           stringsAsFactors = F)
    counter=1
    for(i in list) {
        #Get seizure counts for each day of the week in DST
        #-this is tabulated BY DATE (i.e. all Sz on Sunday 2008-03-16)
        #-this allows for independent t-tests (albeit suboptimal compared to paired t-tests)
        wkdayinDST <- firstweek[which(firstweek$wkday == i),"datetime"]
        wkdaycount <- table(as.Date(wkdayinDST,'America/Los_Angeles'))
        wkdaycountdf <- as.data.frame(wkdaycount)
        wkdayscld <- wkdaycountdf
        wkdayscld$Var1 <- as.Date(as.POSIXct(as.character(wkdayscld$Var1)),'America/Los_Angeles')
        wkdayscld <- merge.data.frame(x=wkdayscld,y=firstscld,all.x=T,sort=F)
        
        #Get seizure counts for each day of the week not in DST
        #-this is tabulated BY DATE (i.e. all Sz on Sunday 2008-03-16)
        wkdaynonDST <- secondweek[which(secondweek$wkday == i),"datetime"]
        wkdaycounts <- table(as.Date(wkdaynonDST,'America/Los_Angeles'))
        wkdaycountsdf <- as.data.frame(wkdaycounts)
        wkday2scld <- wkdaycountsdf
        wkday2scld$Var1 <- as.Date(as.POSIXct(as.character(wkday2scld$Var1)),'America/Los_Angeles')
        wkday2scld <- merge.data.frame(x=wkday2scld,y=secondscld,all.x=T,sort=F)
        
        ###WEIGHTED###
        weightedT <- wtd.t.test(wkday2scld$Freq,wkdayscld$Freq,wkday2scld$AtRiskperDAY,wkdayscld$AtRiskperDAY)
        week2weekstats[counter, "Weekday"] <- i
        week2weekstats[which(week2weekstats$Weekday == i),"FreqT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$Weekday == i),"Freqdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$Weekday == i),"FreqP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(wkday2scld$Freq,wkdayscld$Freq)
        week2weekstats[which(week2weekstats$Weekday == i),"Freqd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$Weekday == i),"COMPmean"] <- wt.mean(wkday2scld$Freq,wkday2scld$AtRiskperDAY)
        print(paste(i,wktwo,"Sz counts 2008-2016 weighted mean:",round(wt.mean(wkday2scld$Freq,wkday2scld$AtRiskperDAY),2)))
        week2weekstats[which(week2weekstats$Weekday == i),"COMPsd"] <- wt.sd(wkday2scld$Freq,wkday2scld$AtRiskperDAY)
        print(paste(i,wktwo,"Sz counts 2008-2016 SD:",round(wt.sd(wkday2scld$Freq,wkday2scld$AtRiskperDAY),2)))
        week2weekstats[which(week2weekstats$Weekday == i),"DSTmean"] <- wt.mean(wkdayscld$Freq,wkdayscld$AtRiskperDAY)
        print(paste(i,wkone,"Sz counts 2008-2016 mean:",round(wt.mean(wkdayscld$Freq,wkdayscld$AtRiskperDAY),2)))
        week2weekstats[which(week2weekstats$Weekday == i),"DSTsd"] <- wt.sd(wkdayscld$Freq,wkdayscld$AtRiskperDAY)
        print(paste(i,wkone,"Sz counts 2008-2016 SD:",round(wt.sd(wkdayscld$Freq,wkdayscld$AtRiskperDAY),2)))
        
        wkday4merge <- wkdayscld
        wkday24merge <- wkday2scld
        wkday4merge$Var1 <- year(wkday4merge$Var1)
        wkday24merge$Var1 <- year(wkday24merge$Var1)
        #x is second week, y is first week (flipped)
        wkdayMERGED <- merge.data.frame(wkday24merge,wkday4merge,by.x="Var1",by.y="Var1",all.x=T)
        wkdayMERGED$RateRatio <- wkdayMERGED$scldIncidenceperDAY.y/wkdayMERGED$scldIncidenceperDAY.x #Rate Ratio from first week (usually DST)/second week (usually comparison week)
        
        baselinerisk <- rep(1,nrow(wkdayscld))
        
        weightedT <- wtd.t.test(wkdayMERGED$RateRatio,baselinerisk,wkdayMERGED$AtRiskperDAY.x,wkdayscld$AtRiskperDAY)
        week2weekstats[which(week2weekstats$Weekday == i),"RRT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$Weekday == i),"RRdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$Weekday == i),"RRP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(wkdayMERGED$RateRatio,baselinerisk)
        week2weekstats[which(week2weekstats$Weekday == i),"RRd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$Weekday == i),"RateRatio"] <- wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)
        print(paste(i,"mean rate ratio of",wkone,"to",wktwo,":",wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)))
        print(paste(i,"SD rate ratio of",wkone,"to",wktwo,":",wt.sd(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)))
        week2weekstats[which(week2weekstats$Weekday == i),"lCI"] <- wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)-1.96*wt.sd(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)/sqrt(length(wkdayMERGED$RateRatio))
        week2weekstats[which(week2weekstats$Weekday == i),"uCI"] <- wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)+1.96*wt.sd(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)/sqrt(length(wkdayMERGED$RateRatio))
        print(paste(i,"95% CI of rate ratio of",wkone,"to",wktwo,":",
                    round(wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)-1.96*wt.sd(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)/sqrt(length(wkdayMERGED$RateRatio)),2),
                    "to",
                    round(wt.mean(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)+1.96*wt.sd(wkdayMERGED$RateRatio,wkdayMERGED$AtRiskperDAY.x)/sqrt(length(wkdayMERGED$RateRatio)),2)))
        
        firstdf[counter,"Week"] <- wkone
        firstdf[counter,"Weekday"] <- i
        firstdf[counter,"Mean_Sz_count"] <- wt.mean(wkdayscld$Freq,wkdayscld$AtRiskperDAY)
        firstdf[counter,"sd"] <- wt.sd(wkdayscld$Freq,wkdayscld$AtRiskperDAY)
        firstdf[counter,"se"] <- wt.sd(wkdayscld$Freq,wkdayscld$AtRiskperDAY)/sqrt(nrow(wkdayscld))
        
        seconddf[counter,"Week"] <- wktwo
        seconddf[counter,"Weekday"] <- i
        seconddf[counter,"Mean_Sz_count"] <- wt.mean(wkday2scld$Freq,wkday2scld$AtRiskperDAY)
        seconddf[counter,"sd"] <- wt.sd(wkday2scld$Freq,wkday2scld$AtRiskperDAY)
        seconddf[counter,"se"] <- wt.sd(wkday2scld$Freq,wkday2scld$AtRiskperDAY)/sqrt(nrow(wkday2scld))
        
        ##Need a week2week for raw data to put into geom_boxplot
        FORweek2week <- data.frame("RateRatio"=wkdayMERGED$RateRatio)
        FORweek2week$"Weekday" <- i
        FORweek2week$"Year" <- wkdayMERGED$Var1
        FORweek2week <- FORweek2week[,c(2,3,1)]
        week2week <- rbind(week2week,FORweek2week)
        
        counter=counter+1
    }
    
    write.table(week2weekstats,
                file = paste("week2week_weekdaySTATS_",wkone,"_",wktwo,".txt",sep=""),
                quote = F,
                row.names = F)
    
    factorlevels <- factor(list,levels=list)
    week2week$Weekday <- factor(week2week$Weekday, levels = factorlevels) #Ensures Weekdays stay in the same order, despite coercing to factors
    
    #Now plot the rate ratios, by weekday
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")],
                     aes(x=Weekday, y=RateRatio),
                     fill="#4271AE",
                     alpha=0.5,
                     outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week,
                   aes(x=Weekday, y=RateRatio, color=factor(Year)),
                   alpha=1,
                   size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",
                      wkone,
                      " to ",
                      wktwo,
                      " over ",
                      min(year(Sz08to16$datetime)),
                      " to ",
                      max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    
    #The above demonstrates pretty extreme outliers (particularly in the first full year...possibly bias from high-documentation rates and low population counts)
    # -Seems reasonable to remove those beyond 3 SD (particularly for the case of the whole-year-as-baseline comparisons)
    week2week <- week2week[which(week2week$RateRatio > (mean(week2week$RateRatio)-3*sd(week2week$RateRatio)) & week2week$RateRatio < (mean(week2week$RateRatio)+3*sd(week2week$RateRatio))),]
    
    #Now plot the rate ratios again with extreme outliers removed
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")],
                     aes(x=Weekday, y=RateRatio),
                     fill="#4271AE",
                     alpha=0.5,
                     outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week,
                   aes(x=Weekday, y=RateRatio, color=factor(Year)),
                   alpha=1,
                   size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",
                      wkone,
                      " to ",
                      wktwo,
                      " over ",
                      min(year(Sz08to16$datetime)),
                      " to ",
                      max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    
    png(paste("Rate Ratios comparing ",wkone," and ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")], aes(x=Weekday, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week, aes(x=Weekday, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",wkone," to ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    dev.off()
    
    firstdf$Weekday <- factor(firstdf$Weekday, levels = firstdf$Weekday) #ensures weekdays stay in order Sun-Sat
    seconddf$Weekday <- factor(seconddf$Weekday, levels = seconddf$Weekday) #ensures weekdays stay in order Sun-Sat
    comparedf <- rbind(firstdf,seconddf)
    
    png(paste("Comparison between ",wkone," and ",wktwo,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot(comparedf, aes(x=Weekday, y=Mean_Sz_count, fill=Week)) + 
        geom_bar(position=position_dodge(), stat="identity",
                 colour="black", # Use black outlines,
                 size=.3) +      # Thinner lines
        #stat_compare_means(aes(group = Week), label = "p.signif", label.y = 300)
        geom_errorbar(aes(ymin=Mean_Sz_count-se, ymax=Mean_Sz_count+se),
                      size=.3,    # Thinner lines
                      width=.2,
                      position=position_dodge(.9)) +
        xlab("Weekday") +
        ylab("Number of seizures (\u00b1SEM)") +
        scale_fill_hue(name=paste(wkone,"vs",wktwo), # Legend label, use darker colors
                       breaks=c(wkone, wktwo),
                       labels=c(wkone, wktwo)) +
        ggtitle("Comparison of seizures on a given weekday") +
        scale_y_continuous(breaks=0:500*100) +
        theme_bw())
    dev.off()
}
```
  
Compare DST to non-DST  
```{r DST to non-DST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofDST,
                secondweek=Sz08to16notDST,
                wkone="week of DST",
                wktwo="all non DST")
```
  
Compare DST to pre-DST  
```{r DST to pre-DST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofDST,
                secondweek=Sz08to16wkpreDST,
                wkone="week of DST",
                wktwo="preDST week")
```
  
Compare DST to the week post-DST week  
```{r DST to post-DST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofDST,
                secondweek=Sz08to16wkpostDST,
                wkone="week of DST",
                wktwo="week after DST week")
```
  
Compare DST to ST  
```{r DST to ST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofDST,
                secondweek=Sz08to16wkofST,
                wkone="week of DST",
                wktwo="ST start week")
```
  
Compare ST to pre-ST  
```{r DST to pre-ST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofST,
                secondweek=Sz08to16wkpreST,
                wkone="week of ST",
                wktwo="preST week")
```
  
Compare ST to the week post-ST week  
```{r DST to post-ST, echo=FALSE}
compareweekdays(firstweek=Sz08to16wkofST,
                secondweek=Sz08to16wkpostST,
                wkone="week of ST",
                wktwo="week after ST week")
```
  
  
Visual demonstration of seizure rates registered to the DST time period  
```{r daily seizure rates graph, echo=FALSE}
Sz4timeplot <- Sz08to16[,c("datetime","DSTday","STday")]
Sz4timeplot$time0 <- yday(Sz08to16$datetime) - Sz08to16$DSTday
summary(Sz4timeplot) #things are now registered to DST's Sunday as t=0
Sz4timeplot$year <- year(Sz08to16$datetime)

table(Sz4timeplot$time0) #Shows that the extreme tails are undersampled (due to variability in onset/offset of DST)...hence usage of SEM
yearlist <- c(min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) #Bound years by the bounds of the dataset
CountsByYear <- data.frame("Index"=seq(min(Sz4timeplot$time0),max(Sz4timeplot$time0),1))
colID <- 2
for(i in yearlist) {
    yearlyCount <- Sz4timeplot[which(year(Sz4timeplot$datetime) == i),"time0"]
    table(yearlyCount)
    CountsByYear <- merge.data.frame(CountsByYear,as.data.frame(t(table(yearlyCount)))[,2:3],by.x="Index",by.y="yearlyCount",all.x = T)
    names(CountsByYear)[colID] <- i
    colID <- colID+1
}
fromcol <- grep(min(year(Sz08to16$datetime)), colnames(CountsByYear))
tocol <- grep(max(year(Sz08to16$datetime)), colnames(CountsByYear))
CountsByYear <- cbind(CountsByYear,
                      Mean=apply(CountsByYear[,fromcol:tocol],1,mean,na.rm=T),
                      SD=apply(CountsByYear[,fromcol:tocol],1,sd,na.rm=T))
for(i in 1:nrow(CountsByYear)) {
    CountsByYear[i,"SEM"] <- CountsByYear[i,"SD"]/sqrt(sum(!is.na(CountsByYear[i,fromcol:tocol])))
}
TallCount <- data.frame("Index"=numeric(),
                        "SzCount"=numeric(),
                        "Year"=numeric())
for(i in yearlist) {
    FORtall <- CountsByYear[,c("Index",i)]
    names(FORtall)[2] <- "SzCount"
    FORtall$Year <- i
    TallCount <- rbind(TallCount,FORtall)
}
#CountsByYear$Mean <- rowMeans(CountsByYear[,fromcol:tocol], na.rm=T)
#SDtemp <- transform(CountsByYear[,fromcol:tocol], SD=apply(CountsByYear[,fromcol:tocol],1,sd,na.rm=T))

png("Yearly trend.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(CountsByYear, aes(x=Index,y=Mean)) + 
    stat_smooth(method="loess", span=7/365, se=TRUE, alpha=0.3) + #using loess smoothing with proportional smoothing from 7 out of 365 days
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=7, xmax=237, ymin=-Inf, ymax=Inf, alpha=0.2, fill="yellow") + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Seizure counts per day (mean \u00b1SEM)") +
    ggtitle(paste("Yearly seizure trends over the period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
    theme_bw())
dev.off()

print(ggplot(CountsByYear, aes(x=Index,y=Mean)) + 
    stat_smooth(method="loess", span=7/365, se=TRUE, alpha=0.3) + #using loess smoothing with proportional smoothing from 7 out of 365 days
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=7, xmax=237, ymin=-Inf, ymax=Inf, alpha=0.2, fill="yellow") + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Seizure counts per day (mean \u00b1SEM)") +
    ggtitle(paste("Yearly seizure trends over the period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
    theme_bw())

###May consider making CountsByYear a tall matrix and then coloring by year using methods from http://ggplot2.tidyverse.org/reference/geom_smooth.html
#library(RColorBrewer)
png("Yearly trend_with points.png", 
    width = 9, 
    height = 6, 
    units = 'in', 
    bg = "transparent", 
    res = 300)
print(ggplot(TallCount, aes(x=Index,y=SzCount,color=Year)) + 
      geom_point() + 
      #scale_x_continuous(breaks = c(cat(yearlist,sep=","))) + 
      #scale_color_brewer(breaks = c(cat(paste(shQuote(yearlist,type="cmd"),collapse=","))),
      #scale_color_brewer(breaks = c(cat(yearlist,sep=",")), palette="Set3") + #http://www.sthda.com/english/wiki/ggplot2-colors-how-to-change-colors-automatically-and-manually
      geom_smooth(method="loess", span=7/365, se=TRUE, alpha=0.3, colour="red") + 
      geom_vline(xintercept=c(0,7,237,244)) + 
      annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
      annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
      xlab("Day of the year (indexed to DST transition)") +
      ylab("Seizure counts per day (mean \u00b1SEM)") +
      ggtitle(paste("Yearly seizure trends over the period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) + 
      ylim(0,quantile(TallCount$SzCount, 0.99, na.rm=T)[[1]]) + 
      theme_bw())
dev.off()

print(ggplot(TallCount, aes(x=Index,y=SzCount,color=Year)) + 
    geom_point() + 
    #scale_x_continuous(breaks = c(cat(yearlist,sep=","))) + 
    #scale_color_brewer(breaks = c(cat(paste(shQuote(yearlist,type="cmd"),collapse=","))),
    #scale_color_brewer(breaks = c(cat(yearlist,sep=",")), palette="Set3") + #http://www.sthda.com/english/wiki/ggplot2-colors-how-to-change-colors-automatically-and-manually
    geom_smooth(method="loess", span=7/365, se=TRUE, alpha=0.3, colour="red") + 
    geom_vline(xintercept=c(0,7,237,244)) + 
    annotate("rect", xmin=0, xmax=7, ymin=-Inf, ymax=Inf, alpha=0.2, fill="red") + 
    annotate("rect", xmin=237, xmax=244, ymin=-Inf, ymax=Inf, alpha=0.2, fill="green") + 
    xlab("Day of the year (indexed to DST transition)") +
    ylab("Seizure counts per day (mean \u00b1SEM)") +
    ggtitle(paste("Yearly seizure trends over the period from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) + 
    ylim(0,quantile(TallCount$SzCount, 0.99, na.rm=T)[[1]]) + 
    theme_bw())
```
  
Weekly comparisons  
#Note: Rate Ratios are calculated as DST incidence/other week incidence (thus RR > 1 => increased risk of seizures in DST, relative to the comparison)  
```{r weekly comparisons}
#Find out what week DST is in, register to that then calculate
#If wanting to do comparison to the every-non-DST-week baseline, then second week must be Sz08to16nonDST/"all non DST"
compareweeks <- function(firstweek=Sz08to16wkofDST,
                         secondweek=Sz08to16notDST,
                         wkone="week of DST",
                         wktwo="all non DST") {
    
    #Get seizure counts for the week in DST
    #-this allows for independent t-tests (albeit suboptimal compared to paired t-tests)
    DSTweekCount <- as.data.frame(table(year(firstweek$datetime)))
    DSTweekNum <- DSTweekCount
    DSTweekNum$Var1 <- as.numeric(seq(from=min(year(firstweek$datetime)),to=max(year(firstweek$datetime)))) #need to make numeric
    DSTweekWeights <- data.frame("Var1"=numeric(),
                                 "Weights"=numeric())
    #generate average weekly counts of AtRisk, for weighted averages
    counter=1
    for(i in min(as.numeric(DSTweekNum$Var1)):max(as.numeric(DSTweekNum$Var1))){
        DSTweekWeights[counter,"Var1"] <- i
        DSTweekWeights[counter,"Weights"] <- mean(firstweek[which(year(firstweek$datetime) == i),"AtRiskperWEEK"])
        counter=counter+1
    }
    
    week2weekstats <- data.frame("epoch"=character(),
                                 "DSTmean"=numeric(),
                                 "DSTsd"=numeric(),
                                 "COMPmean"=numeric(),
                                 "COMPsd"=numeric(),
                                 "FreqP"=numeric(),
                                 "FreqT"=numeric(),
                                 "Freqdf"=numeric(),
                                 "Freqd"=numeric(),
                                 "RateRatio"=numeric(),
                                 "lCI"=numeric(),
                                 "uCI"=numeric(),
                                 "RRP"=numeric(),
                                 "RRT"=numeric(),
                                 "RRdf"=numeric(),
                                 "RRd"=numeric(),
                                 stringsAsFactors = F)
    
    if(identical(secondweek,Sz08to16notDST)) { #For the all-non-DST-weeks-as-baseline comparison
        #Get seizure counts for week(s) not in DST
        NONweekdf <- secondweek[,c("datetime","weeknum","DSTweek")]
        NONweekdf <- NONweekdf[-which(NONweekdf$weeknum == NONweekdf$DSTweek),] #ensures no DST-week counts are included
        NONweekdf$year <- year(NONweekdf$datetime)
        table(NONweekdf$weeknum,NONweekdf$year)
        NONweekCount <- as.data.frame(table(NONweekdf$weeknum,NONweekdf$year))
        NONweekCount[NONweekCount == 0] <- NA #replace non-existing weeks (e.g. year without the 53rd week, DST)
        
        #T-tests (x is for week of DST, y is for comparison week(s)):
        print(t.test(DSTweekCount$Freq,NONweekCount$Freq))
    
        NON4gg <- NONweekCount[,2:3]
        names(NON4gg) <- c("Year","Freq")
        NON4gg$Year <- as.factor(NON4gg$Year)
        DST4gg <- DSTweekCount
        names(DST4gg) <- c("Year","Freq")
        DST4gg$Year <- as.factor(DST4gg$Year)
        
        #Plot it
        print(ggplot() + 
            geom_jitter(data=NON4gg, aes(x=Year,y=Freq), position=position_jitter(width=0.05), alpha=0.8) + #Outliers from incomplete weeks
            geom_boxplot(data=NON4gg, aes(x=Year,y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Outliers from incomplete weeks
            geom_point(data=DST4gg, aes(x=Year,y=Freq), color="red", size=4, shape=18) + 
            xlab("Year") +
            ylab("Seizure Counts (per week)") +
            ggtitle(paste("Percentile for ",wkone," seizure counts, per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
            theme_bw())
        
        png(paste("Percentile for ",wkone," seizure counts, per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
            width = 9, 
            height = 6, 
            units = 'in', 
            bg = "transparent", 
            res = 300)
        print(ggplot() + 
            geom_jitter(data=NON4gg, aes(x=Year,y=Freq), position=position_jitter(width=0.05), alpha=0.8) + #Outliers from incomplete weeks
            geom_boxplot(data=NON4gg, aes(x=Year,y=Freq), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Outliers from incomplete weeks
            geom_point(data=DST4gg, aes(x=Year,y=Freq), color="red", size=4, shape=18) + 
            xlab("Year") +
            ylab("Seizure Counts (per week)") +
            ggtitle(paste("Percentile for ",wkone," seizure counts, per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
            theme_bw())
        dev.off()
        
        #Make Z-score comparison
        Zweek <- data.frame("Year"=numeric(),
                            "PopMean"=numeric(),
                            "PopSD"=numeric(),
                            "SzCount"=numeric(),
                            "Zscore"=numeric(),
                            "Percentile"=numeric())
        counter=1
        for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
            Zweek[counter,"Year"] <- i
            Zweek[counter,"PopMean"] <- mean(na.omit(NONweekCount[which(NONweekCount$Var2 == i),"Freq"]))
            Zweek[counter,"PopSD"] <- sd(na.omit(NONweekCount[which(NONweekCount$Var2 == i),"Freq"]))
            Zweek[counter,"SzCount"] <- DSTweekCount[which(DSTweekCount$Var1 == i),"Freq"]
            Zweek[counter,"Zscore"] <- (Zweek[counter,"SzCount"]-Zweek[counter,"PopMean"])/Zweek[counter,"PopSD"]
            Zweek[counter,"Percentile"] <- round(pnorm(Zweek[counter,"Zscore"])*100,2)
            counter=counter+1
        }
        write.table(Zweek,
                    file = paste("Yearly percentiles by week ",wkone,".txt",sep=""),
                    quote = F,
                    row.names = F)
        Zweek$Year <- as.factor(Zweek$Year)
        #library(ggplot2)

        print(ggplot(Zweek[,c("Year","Percentile")], aes(x=Year, y=Percentile)) + 
            geom_bar(position=position_dodge(), stat="identity",
                     colour="black", # Use black outlines,
                     size=.3) +      # Thinner lines
            geom_hline(yintercept = mean(Zweek$Percentile)) + 
            geom_hline(yintercept = c(mean(Zweek$Percentile)+sd(Zweek$Percentile),
                                      mean(Zweek$Percentile)-sd(Zweek$Percentile)),
                       linetype=3) + 
            xlab("Year") +
            ylab("Percentile") +
            ggtitle(paste("Percentile of seizure counts for ",wkone," per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) +
            scale_y_continuous(breaks=0:100*10, limits=c(0,100)) +
            theme_bw())
        
        png(paste("Percentile of seizure counts for ",wkone," per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
            width = 9, 
            height = 6, 
            units = 'in', 
            bg = "transparent", 
            res = 300)
        print(ggplot(Zweek[,c("Year","Percentile")], aes(x=Year, y=Percentile)) + 
            geom_bar(position=position_dodge(), stat="identity",
                     colour="black", # Use black outlines,
                     size=.3) +      # Thinner lines
            geom_hline(yintercept = mean(Zweek$Percentile)) + 
            geom_hline(yintercept = c(mean(Zweek$Percentile)+sd(Zweek$Percentile),
                                      mean(Zweek$Percentile)-sd(Zweek$Percentile)),
                       linetype=3) + 
            xlab("Year") +
            ylab("Percentile") +
            ggtitle(paste("Percentile of seizure counts for ",wkone," per week from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) +
            scale_y_continuous(breaks=0:100*10, limits=c(0,100)) +
            theme_bw())
        dev.off()
        
        for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
            #Subsetting for the year of interest
            thisyear <- Sz08to16[which(year(Sz08to16$datetime) == i),]
            firstyear <- firstweek[which(year(firstweek$datetime) == i),]
            secondyear <- secondweek[which(year(secondweek$datetime) == i),]
            
            #Try using denominator estimated by number of individuals recording through the end of the period of interest
            firstdenomdf <- Sz08to16[which(Sz08to16$datetime <= as.Date(max(firstyear$datetime),'America/Los_Angeles')),"Unlinked_ID"]
            firstdenom <- length(unique(firstdenomdf))
            baselineweeklist <- na.omit(NONweekCount[which(NONweekCount$Var2 == i),"Var1"])
            
            #Have to do this for each week in the baseline (NON DST) period
            for (j in baselineweeklist) {
                weeksend <- max(as.Date(secondyear[which(epiweek(secondyear$datetime) == as.numeric(j)),"datetime"],'America/Los_Angeles'))
                seconddenomdf <- Sz08to16[which(as.Date(Sz08to16$datetime,'America/Los_Angeles') <= weeksend),"Unlinked_ID"]
                seconddenom <- length(unique(seconddenomdf))
                NONweekCount[which(NONweekCount$Var1 == as.numeric(j) & NONweekCount$Var2 == i),"AtRisk"] <- seconddenom
                NONweekCount[which(NONweekCount$Var1 == as.numeric(j) & NONweekCount$Var2 == i),"Incidence"] <- NONweekCount[which(NONweekCount$Var1 == as.numeric(j) & NONweekCount$Var2 == i),"Freq"]/seconddenom
            }
            NONweekCount[which(NONweekCount$Var2 == i),"DSTFreq"] <- DSTweekCount[which(DSTweekCount$Var1 == i),"Freq"]
            NONweekCount[which(NONweekCount$Var2 == i),"DSTAtRisk"] <- firstdenom
            NONweekCount[which(NONweekCount$Var2 == i),"DSTIncidence"] <- DSTweekCount[which(DSTweekCount$Var1 == i),"Freq"]/firstdenom
            NONweekCount$RateRatio <- NONweekCount$DSTIncidence/NONweekCount$Incidence
            
        }
        
        print(ggplot() + 
            geom_jitter(data=NONweekCount, aes(x=Var2,y=RateRatio), position=position_jitter(width=0.05), alpha=0.8) + #Outliers from incomplete weeks
            geom_boxplot(data=NONweekCount, aes(x=Var2,y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Outliers from incomplete weeks
            xlab("Year") +
            ylab(paste("Rate Ratios (",wkone," vs each week of the year)",sep="")) +
            ggtitle(paste("Comparison of weekly seizure Rate Ratios for",wkone,min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)),sep=" ")) + 
            geom_hline(yintercept = mean(NONweekCount$RateRatio,na.rm=T)) + 
            geom_hline(yintercept = c(mean(NONweekCount$RateRatio,na.rm=T)+1.96*sd(NONweekCount$RateRatio,na.rm=T),
                                      mean(NONweekCount$RateRatio,na.rm=T)-1.96*sd(NONweekCount$RateRatio,na.rm=T)),
                       linetype=3) + 
            ylim((mean(NONweekCount$RateRatio,na.rm=T)-2*sd(NONweekCount$RateRatio,na.rm=T)),(mean(NONweekCount$RateRatio,na.rm=T)+2*sd(NONweekCount$RateRatio,na.rm=T))) + 
            theme_bw())
        
        #Those outliers look quite spurious, so cutting them out at the >3SD threshold and comparing again
        NONweek4gg <- NONweekCount[which(NONweekCount$RateRatio < (mean(NONweekCount$RateRatio,na.rm=T)+3*sd(NONweekCount$RateRatio,na.rm=T)) & NONweekCount$RateRatio > (mean(NONweekCount$RateRatio,na.rm=T)-3*sd(NONweekCount$RateRatio,na.rm=T))),]
        
        print(ggplot() + 
            geom_jitter(data=NONweek4gg, aes(x=Var2,y=RateRatio), position=position_jitter(width=0.05), alpha=0.8) + #Outliers from incomplete weeks
            geom_boxplot(data=NONweek4gg, aes(x=Var2,y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Outliers from incomplete weeks
            xlab("Year") +
            ylab(paste("Rate Ratios (",wkone," vs each week of the year)",sep="")) +
            ggtitle(paste("Comparison of weekly seizure Rate Ratios for",wkone,min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)),sep=" ")) + 
            geom_hline(yintercept = mean(NONweek4gg$RateRatio,na.rm=T)) + 
            geom_hline(yintercept = c(mean(NONweek4gg$RateRatio,na.rm=T)+1.96*sd(NONweek4gg$RateRatio,na.rm=T),
                                      mean(NONweek4gg$RateRatio,na.rm=T)-1.96*sd(NONweek4gg$RateRatio,na.rm=T)),
                       linetype=3) + 
            theme_bw())
        
        png(paste("Comparison of weekly seizure Rate Ratios for ",wkone," from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
            width = 9, 
            height = 6, 
            units = 'in', 
            bg = "transparent", 
            res = 300)
        print(ggplot() + 
            geom_jitter(data=NONweek4gg, aes(x=Var2,y=RateRatio), position=position_jitter(width=0.05), alpha=0.8) + #Outliers from incomplete weeks
            geom_boxplot(data=NONweek4gg, aes(x=Var2,y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Outliers from incomplete weeks
            xlab("Year") +
            ylab(paste("Rate Ratios (",wkone," vs each week of the year)",sep="")) +
            ggtitle(paste("Comparison of weekly seizure Rate Ratios for",wkone,min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)),sep=" ")) + 
            geom_hline(yintercept = mean(NONweek4gg$RateRatio,na.rm=T)) + 
            geom_hline(yintercept = c(mean(NONweek4gg$RateRatio,na.rm=T)+1.96*sd(NONweek4gg$RateRatio,na.rm=T),
                                      mean(NONweek4gg$RateRatio,na.rm=T)-1.96*sd(NONweek4gg$RateRatio,na.rm=T)),
                       linetype=3) + 
            theme_bw())
        dev.off()
        
        names(NONweekCount) <- c("WeekOfYear","Year","Freq","AtRisk","Incidence","DSTFreq","DSTAtRisk","DSTIncidence","RateRatio")
        forttest <- na.omit(NONweekCount)
        
        weightedT <- wtd.t.test(forttest$Freq,unique(forttest$DSTFreq),forttest$AtRisk,unique(forttest$DSTAtRisk))
        week2weekstats[1, "epoch"] <- "all weeks"
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"FreqT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"Freqdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"FreqP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(forttest$Freq,unique(forttest$DSTFreq))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"Freqd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"COMPmean"] <- wt.mean(forttest$Freq,forttest$AtRisk)
        print(paste("All non-DST Sz counts 2008-2016 weighted mean:",round(wt.mean(forttest$Freq,forttest$AtRisk),2)))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"COMPsd"] <- wt.sd(forttest$Freq,forttest$AtRisk)
        print(paste("All non-DST Sz counts 2008-2016 SD:",round(wt.sd(forttest$Freq,forttest$AtRisk),2)))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"DSTmean"] <- wt.mean(unique(forttest$DSTFreq),unique(forttest$DSTAtRisk))
        print(paste("All DST Sz counts 2008-2016 mean:",round(wt.mean(unique(forttest$DSTFreq),unique(forttest$DSTAtRisk)),2)))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"DSTsd"] <- wt.sd(unique(forttest$DSTFreq),unique(forttest$DSTAtRisk))
        print(paste("All DST Sz counts 2008-2016 SD:",round(wt.sd(unique(forttest$DSTFreq),unique(forttest$DSTAtRisk)),2)))
        
        baselinerisk <- rep(1,length(unique(forttest$DSTAtRisk)))
        weightedT <- wtd.t.test(forttest$RateRatio,baselinerisk,forttest$AtRisk,unique(forttest$DSTAtRisk))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"RRT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"RRdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"RRP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(forttest$RateRatio,baselinerisk)
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"RRd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"RateRatio"] <- wt.mean(forttest$RateRatio,forttest$AtRisk)
        print(paste("Mean of rate ratio of all non-DST weeks:",wt.mean(forttest$RateRatio,forttest$AtRisk)))
        print(paste("SD of rate ratio of all non-DST weeks:",wt.sd(forttest$RateRatio,forttest$AtRisk)))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"lCI"] <- wt.mean(forttest$RateRatio,forttest$AtRisk)-1.96*wt.sd(forttest$RateRatio,forttest$AtRisk)/sqrt(length(forttest$RateRatio))
        week2weekstats[which(week2weekstats$epoch == "all weeks"),"uCI"] <- wt.mean(forttest$RateRatio,forttest$AtRisk)+1.96*wt.sd(forttest$RateRatio,forttest$AtRisk)/sqrt(length(forttest$RateRatio))
        print(paste("95% CI of rate ratio of all non-DST weeks:",
                    round(wt.mean(forttest$RateRatio,forttest$AtRisk)-1.96*wt.sd(forttest$RateRatio,forttest$AtRisk)/sqrt(length(forttest$RateRatio)),2),
                    "to",
                    round(wt.mean(forttest$RateRatio,forttest$AtRisk)+1.96*wt.sd(forttest$RateRatio,forttest$AtRisk)/sqrt(length(forttest$RateRatio)),2)))
        
        write.table(week2weekstats,
                    file = paste("week2weekSTATS",wkone,wktwo,sep="_"),
                    quote = F,
                    row.names = F)
        
        write.table(NONweekCount,
                    file = "Rate Ratios for each week.txt",
                    quote = F,
                    row.names = F)
        
        
    } else { #For the single-week-as-baseline comparisons
        #Get seizure counts for weeks not in DST
        NONweekCount <- as.data.frame(table(year(secondweek$datetime)))
        NONweekNum <- NONweekCount
        NONweekNum$Var1 <- as.numeric(seq(from=min(year(secondweek$datetime)),to=max(year(secondweek$datetime)))) #need to make numeric
        NONweekWeights <- data.frame("Var1"=numeric(),
                                     "Weights"=numeric())
        #generate average weekly counts of AtRisk, for weighted averages
        counter=1
        for(i in min(as.numeric(NONweekNum$Var1)):max(as.numeric(NONweekNum$Var1))){
            NONweekWeights[counter,"Var1"] <- i
            NONweekWeights[counter,"Weights"] <- mean(secondweek[which(year(secondweek$datetime) == i),"AtRiskperWEEK"])
            counter=counter+1
        }
        
        ###WAS NOT WEIGHTED###
        #T-tests (x is for week of DST, y is for comparison week(s)):
        #print(t.test(DSTweekCount$Freq,NONweekCount$Freq))
        #print(cohen.d(DSTweekCount$Freq,NONweekCount$Freq))
        #print(paste(wkone,"Sz counts 2008-2016 mean:",round(mean(DSTweekCount$Freq),2)))
        #print(paste(wkone,"Sz counts 2008-2016 SD:",round(sd(DSTweekCount$Freq),2)))
        #print(paste(wktwo,"Sz counts 2008-2016 mean:",round(mean(NONweekCount$Freq),2)))
        #print(paste(wktwo,"Sz counts 2008-2016 SD:",round(sd(NONweekCount$Freq),2)))
        
        ###WEIGHTED###
        #weightedT <- wtd.t.test(NONweekCount$Freq,DSTweekCount$Freq,NONweekWeights$Weights,DSTweekWeights$Weights)
        #week2weekstats[1, "epoch"] <- wktwo
        #week2weekstats[which(week2weekstats$epoch == wktwo),"FreqT"] <- weightedT$coefficients[[1]]
        #week2weekstats[which(week2weekstats$epoch == wktwo),"Freqdf"] <- weightedT$coefficients[[2]]
        #week2weekstats[which(week2weekstats$epoch == wktwo),"FreqP"] <- weightedT$coefficients[[3]]
        #print(weightedT)
        #CohenD <- cohen.d(NONweekCount$Freq,DSTweekCount$Freq)
        #week2weekstats[which(week2weekstats$epoch == wktwo),"Freqd"] <- CohenD$estimate[[1]]
        #print(CohenD)
        #week2weekstats[which(week2weekstats$epoch == wktwo),"COMPmean"] <- wt.mean(NONweekCount$Freq,NONweekWeights$Weights)
        #print(paste("All non-DST Sz counts 2008-2016 weighted mean:",round(wt.mean(NONweekCount$Freq,NONweekWeights$Weights),2)))
        #week2weekstats[which(week2weekstats$epoch == wktwo),"COMPsd"] <- wt.sd(NONweekCount$Freq,NONweekWeights$Weights)
        #print(paste("All non-DST Sz counts 2008-2016 SD:",round(wt.sd(NONweekCount$Freq,NONweekWeights$Weights),2)))
        #week2weekstats[which(week2weekstats$epoch == wktwo),"DSTmean"] <- wt.mean(DSTweekCount$Freq,DSTweekWeights$Weights)
        #print(paste("All DST Sz counts 2008-2016 mean:",round(wt.mean(DSTweekCount$Freq,DSTweekWeights$Weights),2)))
        #week2weekstats[which(week2weekstats$epoch == wktwo),"DSTsd"] <- wt.sd(DSTweekCount$Freq,DSTweekWeights$Weights)
        #print(paste("All DST Sz counts 2008-2016 SD:",round(wt.sd(DSTweekCount$Freq,DSTweekWeights$Weights),2)))
        
        week2week <- data.frame("Year"=numeric(),
                                "DSTSzcount"=numeric(),
                                "DSTatrisk"=numeric(),
                                "DSTincidence"=numeric(),
                                "NONSzcount"=numeric(),
                                "NONatrisk"=numeric(),
                                "NONincidence"=numeric(),
                                "RateRatio"=numeric())
        counter=1
        for(i in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
            #Subsetting for the year of interest
            thisyear <- Sz08to16[which(year(Sz08to16$datetime) == i),]
            firstyear <- firstweek[which(year(firstweek$datetime) == i),]
            secondyear <- secondweek[which(year(secondweek$datetime) == i),]
            
            #Try using denominator estimated by number of individuals recording through the end of the period of interest
            firstdenomdf <- Sz08to16[which(Sz08to16$datetime <= as.Date(max(firstyear$datetime),'America/Los_Angeles')),"Unlinked_ID"]
            firstdenom <- length(unique(firstdenomdf))
            seconddenomdf <- Sz08to16[which(Sz08to16$datetime <= as.Date(max(secondyear$datetime),'America/Los_Angeles')),"Unlinked_ID"]
            seconddenom <- length(unique(seconddenomdf))
            print(paste("Rough estimate of difference in 'at risk' individuals: ",abs(firstdenom-seconddenom),"; with ",firstdenom," accumulated individuals by DST week of ",i,sep=""))
            
            week2week[counter,"Year"] <- i
            #week2week[counter,"DSTSzcount"] <- DSTweekCount[which(DSTweekCount$Var1 == i),"Freq"]
            #week2week[counter,"DSTatrisk"] <- firstdenom
            #week2week[counter,"DSTincidence"] <- week2week[counter,"DSTSzcount"]/week2week[counter,"DSTatrisk"]
            #week2week[counter,"NONSzcount"] <- NONweekCount[which(NONweekCount$Var1 == i),"Freq"]
            #week2week[counter,"NONatrisk"] <- seconddenom
            #week2week[counter,"NONincidence"] <- week2week[counter,"NONSzcount"]/week2week[counter,"NONatrisk"]
            #week2week[counter,"RateRatio"] <- week2week[counter,"DSTincidence"]/week2week[counter,"NONincidence"]
            week2week[counter,"DSTSzcount"] <- DSTweekCount[which(DSTweekCount$Var1 == i),"Freq"]
            week2week[counter,"DSTatrisk"] <- mean(firstweek[which(year(firstweek$datetime) == i),"AtRiskperWEEK"])
            week2week[counter,"DSTincidence"] <- mean(firstweek[which(year(firstweek$datetime) == i),"scldIncidenceperWEEK"])
            week2week[counter,"NONSzcount"] <- NONweekCount[which(NONweekCount$Var1 == i),"Freq"]
            week2week[counter,"NONatrisk"] <- mean(secondweek[which(year(secondweek$datetime) == i),"AtRiskperWEEK"])
            week2week[counter,"NONincidence"] <- mean(secondweek[which(year(secondweek$datetime) == i),"scldIncidenceperWEEK"])
            week2week[counter,"RateRatio"] <- week2week[counter,"DSTincidence"]/week2week[counter,"NONincidence"]
            counter=counter+1
            
        }
        baselinerisk=rep(1,length(week2week$RateRatio)) #As DST is the reference, we're comparing to this
        ###WAS NOT WEIGHTED###
        #print(t.test(week2week$RateRatio,baselinerisk))
        #print(cohen.d(week2week$RateRatio,baselinerisk))
        #print(paste(wktwo,"rate ratios 2008-2016 mean:",round(mean(week2week$RateRatio),2)))
        #print(paste(wktwo,"rate ratios 2008-2016 SD:",round(sd(week2week$RateRatio),2)))
        #print(paste(wktwo,
        #            "rate ratio conidence interval:",
        #            round(mean(week2week$RateRatio)-1.96*sd(week2week$RateRatio)/sqrt(length(week2week$RateRatio)),2),
        #            "to",
        #            round(mean(week2week$RateRatio)+1.96*sd(week2week$RateRatio)/sqrt(length(week2week$RateRatio)),2)))
        
        ###WEIGHTED###
        weightedT <- wtd.t.test(week2week$NONSzcount,week2week$DSTSzcount,week2week$NONatrisk,week2week$DSTatrisk)
        week2weekstats[1, "epoch"] <- wktwo
        week2weekstats[which(week2weekstats$epoch == wktwo),"FreqT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$epoch == wktwo),"Freqdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$epoch == wktwo),"FreqP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(week2week$NONSzcount,week2week$DSTSzcount)
        week2weekstats[which(week2weekstats$epoch == wktwo),"Freqd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$epoch == wktwo),"COMPmean"] <- wt.mean(week2week$NONSzcount,week2week$NONatrisk)
        print(paste("All",wktwo,"Sz counts 2008-2016 weighted mean:",round(wt.mean(week2week$NONSzcount,week2week$NONatrisk),2)))
        week2weekstats[which(week2weekstats$epoch == wktwo),"COMPsd"] <- wt.sd(week2week$NONSzcount,week2week$NONatrisk)
        print(paste("All",wktwo,"Sz counts 2008-2016 SD:",round(wt.sd(week2week$NONSzcount,week2week$NONatrisk),2)))
        week2weekstats[which(week2weekstats$epoch == wktwo),"DSTmean"] <- wt.mean(week2week$DSTSzcount,week2week$DSTatrisk)
        print(paste("All",wkone,"Sz counts 2008-2016 mean:",round(wt.mean(week2week$DSTSzcount,week2week$DSTatrisk),2)))
        week2weekstats[which(week2weekstats$epoch == wktwo),"DSTsd"] <- wt.sd(week2week$DSTSzcount,week2week$DSTatrisk)
        print(paste("All",wkone,"Sz counts 2008-2016 SD:",round(wt.sd(week2week$DSTSzcount,week2week$DSTatrisk),2)))
        
        weightedT <- wtd.t.test(week2week$RateRatio,baselinerisk,week2week$NONatrisk,week2week$DSTatrisk)
        week2weekstats[which(week2weekstats$epoch == wktwo),"RRT"] <- weightedT$coefficients[[1]]
        week2weekstats[which(week2weekstats$epoch == wktwo),"RRdf"] <- weightedT$coefficients[[2]]
        week2weekstats[which(week2weekstats$epoch == wktwo),"RRP"] <- weightedT$coefficients[[3]]
        print(weightedT)
        CohenD <- cohen.d(week2week$RateRatio,baselinerisk)
        week2weekstats[which(week2weekstats$epoch == wktwo),"RRd"] <- CohenD$estimate[[1]]
        print(CohenD)
        week2weekstats[which(week2weekstats$epoch == wktwo),"RateRatio"] <- wt.mean(week2week$RateRatio,week2week$NONatrisk)
        print(paste("Mean of rate ratio of",wkone,"to",wktwo,":",wt.mean(week2week$RateRatio,week2week$NONatrisk)))
        print(paste("SD of rate ratio of",wkone,"to",wktwo,":",wt.sd(week2week$RateRatio,week2week$NONatrisk)))
        week2weekstats[which(week2weekstats$epoch == wktwo),"lCI"] <- wt.mean(week2week$RateRatio,week2week$NONatrisk)-1.96*wt.sd(week2week$RateRatio,week2week$NONatrisk)/sqrt(length(week2week$RateRatio))
        week2weekstats[which(week2weekstats$epoch == wktwo),"uCI"] <- wt.mean(week2week$RateRatio,week2week$NONatrisk)+1.96*wt.sd(week2week$RateRatio,week2week$NONatrisk)/sqrt(length(week2week$RateRatio))
        print(paste("95% CI of rate ratio of",wkone,"to",wktwo,":",
                    round(wt.mean(week2week$RateRatio,week2week$NONatrisk)-1.96*wt.sd(week2week$RateRatio,week2week$NONatrisk)/sqrt(length(week2week$RateRatio)),2),
                    "to",
                    round(wt.mean(week2week$RateRatio,week2week$NONatrisk)+1.96*wt.sd(week2week$RateRatio,week2week$NONatrisk)/sqrt(length(week2week$RateRatio)),2)))
        
        write.table(week2weekstats,
                    file = paste("week2week_fullweekSTATS_",wkone,"_",wktwo,".txt",sep=""),
                    quote = F,
                    row.names = F)
        
        write.table(week2week,
                    file=paste("Seizure Rate Ratios for ",wkone," compared to ",wktwo,".txt",sep=""),
                    quote = F,
                    row.names = F)
        week2week$Year <- as.factor(week2week$Year)
        
        #Now plot the rate ratios, by year
        print(ggplot(week2week[,c("Year","RateRatio")], aes(x=Year, y=RateRatio)) + 
            #IF WANT AS HISTOGRAM:
            #geom_bar(position=position_dodge(), stat="identity",
            #         colour="black", # Use black outlines,
            #         size=.3) +      # Thinner lines
            geom_point(size=5, color="turquoise4") + 
            geom_hline(yintercept = mean(week2week$RateRatio)) + 
            geom_hline(yintercept = c(mean(week2week$RateRatio)+1.96*sd(week2week$RateRatio),
                                      mean(week2week$RateRatio)-1.96*sd(week2week$RateRatio)),
                       linetype=3) + 
            scale_y_continuous(limits = c(0.5,1.5)) + 
            xlab("Year") +
            ylab("Rate Ratio") +
            ggtitle(paste(wkone,"vs",wktwo,"Rate Ratios from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
            theme_bw())
        png(paste(wkone," vs ",wktwo," Rate Ratios from ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
            width = 9, 
            height = 6, 
            units = 'in', 
            bg = "transparent", 
            res = 300)
        print(ggplot(week2week[,c("Year","RateRatio")], aes(x=Year, y=RateRatio)) + 
            #IF WANT AS HISTOGRAM:
            #geom_bar(position=position_dodge(), stat="identity",
            #         colour="black", # Use black outlines,
            #         size=.3) +      # Thinner lines
            geom_point(size=5, color="turquoise4") + 
            geom_hline(yintercept = mean(week2week$RateRatio)) + 
            geom_hline(yintercept = c(mean(week2week$RateRatio)+1.96*sd(week2week$RateRatio),
                                      mean(week2week$RateRatio)-1.96*sd(week2week$RateRatio)),
                       linetype=3) + 
            scale_y_continuous(limits = c(0.5,1.5)) + 
            xlab("Year") +
            ylab("Rate Ratio") +
            ggtitle(paste(wkone,"vs",wktwo,"Rate Ratios from",min(year(Sz08to16$datetime)),"to",max(year(Sz08to16$datetime)))) +
            theme_bw())
        dev.off()
    }
}
```
  
Compare DST to non-DST  
```{r DST to non-DST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofDST,
             secondweek=Sz08to16notDST,
             wkone="week of DST",
             wktwo="all non DST")
```
  
Compare DST to pre-DST  
```{r DST to pre-DST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofDST,
             secondweek=Sz08to16wkpreDST,
             wkone="week of DST",
             wktwo="preDST week")
```
  
Compare DST to the week post-DST week  
```{r DST to post-DST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofDST,
             secondweek=Sz08to16wkpostDST,
             wkone="week of DST",
             wktwo="week after DST week")
```
  
Compare DST to ST  
```{r DST to ST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofDST,
             secondweek=Sz08to16wkofST,
             wkone="week of DST",
             wktwo="ST start week")
```

  
Compare ST to pre-ST  
```{r DST to pre-ST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofST,
             secondweek=Sz08to16wkpreST,
             wkone="week of ST",
             wktwo="preST week")
```
  
Compare ST to the week post-ST week  
```{r DST to post-ST again, echo=FALSE}
compareweeks(firstweek=Sz08to16wkofST,
             secondweek=Sz08to16wkpostST,
             wkone="week of ST",
             wktwo="week after ST week")
```

```{r scratchpad, eval=FALSE, echo=FALSE}
###Prior compareweeks function (first function contents)###
    #Get seizure counts for each day of the week in DST
    #-this is tabulated BY DATE (i.e. all Sz on Sunday 2008-03-16)
    #-this allows for independent t-tests (albeit suboptimal compared to paired t-tests)
    SUNinDST <- firstweek[which(firstweek$wkday == "Sunday"),"datetime"]
    SUNcount <- table(as.Date(SUNinDST,'America/Los_Angeles'))
    SUNcountdf <- as.data.frame(SUNcount)
    MONinDST <- firstweek[which(firstweek$wkday == "Monday"),"datetime"]
    MONcount <- table(as.Date(MONinDST,'America/Los_Angeles'))
    MONcountdf <- as.data.frame(MONcount)
    TUEinDST <- firstweek[which(firstweek$wkday == "Tuesday"),"datetime"]
    TUEcount <- table(as.Date(TUEinDST,'America/Los_Angeles'))
    TUEcountdf <- as.data.frame(TUEcount)
    WEDinDST <- firstweek[which(firstweek$wkday == "Wednesday"),"datetime"]
    WEDcount <- table(as.Date(WEDinDST,'America/Los_Angeles'))
    WEDcountdf <- as.data.frame(WEDcount)
    THUinDST <- firstweek[which(firstweek$wkday == "Thursday"),"datetime"]
    THUcount <- table(as.Date(THUinDST,'America/Los_Angeles'))
    THUcountdf <- as.data.frame(THUcount)
    FRIinDST <- firstweek[which(firstweek$wkday == "Friday"),"datetime"]
    FRIcount <- table(as.Date(FRIinDST,'America/Los_Angeles'))
    FRIcountdf <- as.data.frame(FRIcount)
    SATinDST <- firstweek[which(firstweek$wkday == "Saturday"),"datetime"]
    SATcount <- table(as.Date(SATinDST,'America/Los_Angeles'))
    SATcountdf <- as.data.frame(SATcount)
    
    #Get seizure counts for each day of the week not in DST
    #-this is tabulated BY DATE (i.e. all Sz on Sunday 2008-03-16)
    SUNnonDST <- secondweek[which(secondweek$wkday == "Sunday"),"datetime"]
    SUNcounts <- table(as.Date(SUNnonDST,'America/Los_Angeles'))
    SUNcountsdf <- as.data.frame(SUNcounts)
    MONnonDST <- secondweek[which(secondweek$wkday == "Monday"),"datetime"]
    MONcounts <- table(as.Date(MONnonDST,'America/Los_Angeles'))
    MONcountsdf <- as.data.frame(MONcounts)
    TUEnonDST <- secondweek[which(secondweek$wkday == "Tuesday"),"datetime"]
    TUEcounts <- table(as.Date(TUEnonDST,'America/Los_Angeles'))
    TUEcountsdf <- as.data.frame(TUEcounts)
    WEDnonDST <- secondweek[which(secondweek$wkday == "Wednesday"),"datetime"]
    WEDcounts <- table(as.Date(WEDnonDST,'America/Los_Angeles'))
    WEDcountsdf <- as.data.frame(WEDcounts)
    THUnonDST <- secondweek[which(secondweek$wkday == "Thursday"),"datetime"]
    THUcounts <- table(as.Date(THUnonDST,'America/Los_Angeles'))
    THUcountsdf <- as.data.frame(THUcounts)
    FRInonDST <- secondweek[which(secondweek$wkday == "Friday"),"datetime"]
    FRIcounts <- table(as.Date(FRInonDST,'America/Los_Angeles'))
    FRIcountsdf <- as.data.frame(FRIcounts)
    SATnonDST <- secondweek[which(secondweek$wkday == "Saturday"),"datetime"]
    SATcounts <- table(as.Date(SATnonDST,'America/Los_Angeles'))
    SATcountsdf <- as.data.frame(SATcounts)
    
    #T-tests (x is for weekdays in DST, y is for comparison weeks):
    print(SunT <- t.test(SUNcount,SUNcounts))
    print(cohen.d(as.data.frame(SUNcount)$Freq,as.data.frame(SUNcounts)$Freq))
    print(paste(wkone,"Sunday Sz counts 2008-2016 mean:",round(mean(as.data.frame(SUNcount)$Freq),2)))
    print(paste(wkone,"Sunday Sz counts 2008-2016 SD:",round(sd(as.data.frame(SUNcount)$Freq),2)))
    print(paste(wktwo,"Sunday Sz counts 2008-2016 mean:",round(mean(as.data.frame(SUNcounts)$Freq),2)))
    print(paste(wktwo,"Sunday Sz counts 2008-2016 SD:",round(sd(as.data.frame(SUNcounts)$Freq),2)))
    
    print(MonT <- t.test(MONcount,MONcounts))
    print(cohen.d(as.data.frame(MONcount)$Freq,as.data.frame(MONcounts)$Freq))
    print(paste(wkone,"Monday Sz counts 2008-2016 mean:",round(mean(as.data.frame(MONcount)$Freq),2)))
    print(paste(wkone,"Monday Sz counts 2008-2016 SD:",round(sd(as.data.frame(MONcount)$Freq),2)))
    print(paste(wktwo,"Monday Sz counts 2008-2016 mean:",round(mean(as.data.frame(MONcounts)$Freq),2)))
    print(paste(wktwo,"Monday Sz counts 2008-2016 SD:",round(sd(as.data.frame(MONcounts)$Freq),2)))
    
    print(TueT <- t.test(TUEcount,TUEcounts))
    print(cohen.d(as.data.frame(TUEcount)$Freq,as.data.frame(TUEcounts)$Freq))
    print(paste(wkone,"Tuesday Sz counts 2008-2016 mean:",round(mean(as.data.frame(TUEcount)$Freq),2)))
    print(paste(wkone,"Tuesday Sz counts 2008-2016 SD:",round(sd(as.data.frame(TUEcount)$Freq),2)))
    print(paste(wktwo,"Tuesday Sz counts 2008-2016 mean:",round(mean(as.data.frame(TUEcounts)$Freq),2)))
    print(paste(wktwo,"Tuesday Sz counts 2008-2016 SD:",round(sd(as.data.frame(TUEcounts)$Freq),2)))
    
    print(WedT <- t.test(WEDcount,WEDcounts))
    print(cohen.d(as.data.frame(WEDcount)$Freq,as.data.frame(WEDcounts)$Freq))
    print(paste(wkone,"Wednesday Sz counts 2008-2016 mean:",round(mean(as.data.frame(WEDcount)$Freq),2)))
    print(paste(wkone,"Wednesday Sz counts 2008-2016 SD:",round(sd(as.data.frame(WEDcount)$Freq),2)))
    print(paste(wktwo,"Wednesday Sz counts 2008-2016 mean:",round(mean(as.data.frame(WEDcounts)$Freq),2)))
    print(paste(wktwo,"Wednesday Sz counts 2008-2016 SD:",round(sd(as.data.frame(WEDcounts)$Freq),2)))
    
    print(ThuT <- t.test(THUcount,THUcounts))
    print(cohen.d(as.data.frame(THUcount)$Freq,as.data.frame(THUcounts)$Freq))
    print(paste(wkone,"Thursday Sz counts 2008-2016 mean:",round(mean(as.data.frame(THUcount)$Freq),2)))
    print(paste(wkone,"Thursday Sz counts 2008-2016 SD:",round(sd(as.data.frame(THUcount)$Freq),2)))
    print(paste(wktwo,"Thursday Sz counts 2008-2016 mean:",round(mean(as.data.frame(THUcounts)$Freq),2)))
    print(paste(wktwo,"Thursday Sz counts 2008-2016 SD:",round(sd(as.data.frame(THUcounts)$Freq),2)))
    
    print(FriT <- t.test(FRIcount,FRIcounts))
    print(cohen.d(as.data.frame(FRIcount)$Freq,as.data.frame(FRIcounts)$Freq))
    print(paste(wkone,"Friday Sz counts 2008-2016 mean:",round(mean(as.data.frame(FRIcount)$Freq),2)))
    print(paste(wkone,"Friday Sz counts 2008-2016 SD:",round(sd(as.data.frame(FRIcount)$Freq),2)))
    print(paste(wktwo,"Friday Sz counts 2008-2016 mean:",round(mean(as.data.frame(FRIcounts)$Freq),2)))
    print(paste(wktwo,"Friday Sz counts 2008-2016 SD:",round(sd(as.data.frame(FRIcounts)$Freq),2)))
    
    print(SatT <- t.test(SATcount,SATcounts))
    print(cohen.d(as.data.frame(SATcount)$Freq,as.data.frame(SATcounts)$Freq))
    print(paste(wkone,"Saturday Sz counts 2008-2016 mean:",round(mean(as.data.frame(SATcount)$Freq),2)))
    print(paste(wkone,"Saturday Sz counts 2008-2016 SD:",round(sd(as.data.frame(SATcount)$Freq),2)))
    print(paste(wktwo,"Saturday Sz counts 2008-2016 mean:",round(mean(as.data.frame(SATcounts)$Freq),2)))
    print(paste(wktwo,"Saturday Sz counts 2008-2016 SD:",round(sd(as.data.frame(SATcounts)$Freq),2)))
    
    #Getting person-count approximate denominators and incidence rates for each day
    # -note this denominator of person-time is inaccurate for multiple reasons:
    #  +it counts people "at risk" only if they've documented a seizure - i.e. ascertainment bias for those reporting
    #  +it doesn't account for single documenters that then stop using the app - also an ascertainment bias
    #  +it doesn't account for interventions (i.e. surgery, changes in regimen), assuming similar risk over similar time periods
    #  +it doesn't account for "voyeurs" - people who signed up, but haven't documented yet
    
    #Creating list of count data frames
    l.df <- lapply(ls(pattern="[A-Z]countdf"), function(x) get(x))
    l.df <- append(l.df, lapply(ls(pattern="[A-Z]countsdf"), function(x) get(x)))
    #Getting names of environmental variables to name the list elements
    DSTnames <- ls(pattern="[A-Z]countdf")
    NONnames <- ls(pattern="[A-Z]countsdf")
    listnames <- c(DSTnames,NONnames)
    names(l.df) <- listnames
    
    for(i in listnames) {
        #This will add in the relevant data
        for(j in 1:nrow(l.df[[i]])) {
            denomdf <- Sz08to16[which(Sz08to16$datetime <= as.Date(l.df[[i]][j,"Var1"])),"Unlinked_ID"]
            l.df[[i]][j,"AtRisk"] <- length(unique(denomdf))
            l.df[[i]][j,"Incidence"] <- l.df[[i]][j,"Freq"]/length(unique(denomdf))
        }
    }
    
    #For each non-DST data frame add in DST variables and calculate Rate Ratios
    for(i in NONnames) {
        DST4NON <- grep(paste("^",substr(i,1,3),sep=""),DSTnames,value=T) #Get name of comparable DST week
        for(j in 1:nrow(l.df[[i]])) { #Iterate over dates in non-DST data frame
            for(k in 1:nrow(l.df[[DST4NON]])) { #Iterate over dates in DST data frame to add comparisons to non-DST data frame
                if(year(l.df[[i]][j,"Var1"]) == year(l.df[[DST4NON]][k,"Var1"])) { 
                    l.df[[i]][j,"DSTFreq"] <- l.df[[DST4NON]][k,"Freq"] 
                    l.df[[i]][j,"DSTAtRisk"] <- l.df[[DST4NON]][k,"AtRisk"] 
                    l.df[[i]][j,"DSTIncidence"] <- l.df[[DST4NON]][k,"Incidence"] 
                }
            }
        }
        l.df[[i]][,"RateRatio"] <- l.df[[i]][,"DSTIncidence"]/l.df[[i]][,"Incidence"] #Calculate Rate Ratios
    }
    
    #Put the new data frames back into the Global Environment
    list2env(l.df,envir=.GlobalEnv)
    
    week2week <- data.frame("Weekday"=character(),
                            "Year"=numeric(),
                            "RateRatio"=numeric(),
                            stringsAsFactors = F)
    
    for(i in list) {
        weekdaydf <- grep(paste("^",substr(i,1,3),sep=""),NONnames,value=T,ignore.case=T)
        for(j in min(year(Sz08to16$datetime)):max(year(Sz08to16$datetime))) {
            FORweek2week <- data.frame("RateRatio"=l.df[[weekdaydf]][which(year(as.Date(l.df[[weekdaydf]][,"Var1"])) == j),"RateRatio"])
            FORweek2week$"Weekday" <- i
            FORweek2week$"Year" <- j
            FORweek2week <- FORweek2week[,c(2,3,1)]
            week2week <- rbind(week2week,FORweek2week)
        }
    }
    
    DSTbaseline=rep(1,max(week2week$Year)-min(week2week$Year)+1)
    for(i in list) {
        print(t.test(week2week[which(week2week$Weekday == i),"RateRatio"],DSTbaseline))
        print(cohen.d(week2week[which(week2week$Weekday == i),"RateRatio"],DSTbaseline))
        print(paste(wktwo,i,"rate ratios 2008-2016 mean:",
                    round(mean(week2week[which(week2week$Weekday == i),"RateRatio"]),2)))
        print(paste(wktwo,i,"rate ratios 2008-2016 SD:",
                    round(sd(week2week[which(week2week$Weekday == i),"RateRatio"]),2)))
        print(paste(wktwo,
                    i,
                    "rate ratio conidence interval:",
                    round(mean(week2week[which(week2week$Weekday == i),"RateRatio"])-1.96*sd(week2week[which(week2week$Weekday == i),"RateRatio"])/sqrt(length(week2week[which(week2week$Weekday == i),"RateRatio"])),2),
                    "to",
                    round(mean(week2week[which(week2week$Weekday == i),"RateRatio"])+1.96*sd(week2week[which(week2week$Weekday == i),"RateRatio"])/sqrt(length(week2week[which(week2week$Weekday == i),"RateRatio"])),2)))
    }
    
    factorlevels <- factor(list,levels=list)
    week2week$Weekday <- factor(week2week$Weekday, levels = factorlevels) #Ensures Weekdays stay in the same order, despite coercing to factors
    write.table(week2week,
                file=paste("Weekday seizure Rate Ratios for ",wkone," compared to ",wktwo,".txt",sep=""),
                quote = F,
                row.names = F)
    
    #Now plot the rate ratios, by weekday
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")], aes(x=Weekday, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week, aes(x=Weekday, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",wkone," to ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    
    #The above demonstrates pretty extreme outliers (particularly in the first full year...possibly bias from high-documentation rates and low population counts)
    # -Seems reasonable to remove those beyond 3 SD (particularly for the case of the whole-year-as-baseline comparisons)
    week2week <- week2week[which(week2week$RateRatio > (mean(week2week$RateRatio)-3*sd(week2week$RateRatio)) & week2week$RateRatio < (mean(week2week$RateRatio)+3*sd(week2week$RateRatio))),]
    
    #Now plot the rate ratios again with extreme outliers removed
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")], aes(x=Weekday, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week, aes(x=Weekday, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",wkone," to ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    
    png(paste("Rate Ratios comparing ",wkone," and ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot() + 
        geom_boxplot(data=week2week[,c("Weekday","RateRatio")], aes(x=Weekday, y=RateRatio), fill="#4271AE", alpha=0.5, outlier.size=-1) + #Avoid duplicate outlier plotting
        geom_point(data=week2week, aes(x=Weekday, y=RateRatio, color=factor(Year)), alpha=1, size=3) +
        geom_hline(yintercept = mean(week2week$RateRatio,na.rm=T)) + 
        geom_hline(yintercept = c(mean(week2week$RateRatio,na.rm=T)+1.96*sd(week2week$RateRatio,na.rm=T),
                                  mean(week2week$RateRatio,na.rm=T)-1.96*sd(week2week$RateRatio,na.rm=T)),
                   linetype=3) + 
        xlab("Weekday") +
        ylab(paste("Rate Ratio (Sz incidence in ",wkone," vs ",wktwo,")",sep="")) +
        ggtitle(paste("Boxplot for seizure Rate Ratios comparing ",wkone," to ",wktwo," over ",min(year(Sz08to16$datetime))," to ",max(year(Sz08to16$datetime)),sep="")) + 
        theme_bw() + 
        theme(legend.title = element_blank()))
    dev.off()
    
    firstdf <- data.frame("Week"=character(),
                          "Weekday"=character(),
                          "Mean_Sz_count"=numeric(),
                          "sd"=numeric(),
                          "se"=numeric(),
                          stringsAsFactors = F)
    seconddf <- data.frame("Week"=character(),
                           "Weekday"=character(),
                           "Mean_Sz_count"=numeric(),
                           "sd"=numeric(),
                           "se"=numeric(),
                           stringsAsFactors = F)
    sigdf <- data.frame("Weekday"=character(),
                        "p"=numeric(),
                        "p.signif"=character(),
                        stringsAsFactors = F)
    
    index=1
    for(i in list) {
        firstdf[index,"Week"] <- wkone
        firstdf[index,"Weekday"] <- i
        firstdf[index,"Mean_Sz_count"] <- mean(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')))
        firstdf[index,"sd"] <- sd(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')))
        firstdf[index,"se"] <- sd(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')))/sqrt(table(firstweek$wkday)[[i]])
        
        seconddf[index,"Week"] <- wktwo
        seconddf[index,"Weekday"] <- i
        seconddf[index,"Mean_Sz_count"] <- mean(table(as.Date(secondweek[which(secondweek$wkday == i),"datetime"],'America/Los_Angeles')))
        seconddf[index,"sd"] <- sd(table(as.Date(secondweek[which(secondweek$wkday == i),"datetime"],'America/Los_Angeles')))
        seconddf[index,"se"] <- sd(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')))/sqrt(table(secondweek$wkday)[[i]])
        
        sigdf[index,"Weekday"] <- i
        sigdf[index,"p"] <- round(t.test(table(as.Date(firstweek[which(firstweek$wkday == i),"datetime"],'America/Los_Angeles')),
                                         table(as.Date(secondweek[which(secondweek$wkday == i),"datetime"],'America/Los_Angeles')))[["p.value"]],4)
        if(sigdf[index,"p"]<0.05 & sigdf[index,"p"]>0.01) {
            sigdf[index,"p.signif"] <- "*"
        } else if(sigdf[index,"p"]<0.01 & sigdf[index,"p"]>0.001) {
            sigdf[index,"p.signif"] <- "**"
        } else if(sigdf[index,"p"]<0.001) {
            sigdf[index,"p.signif"] <- "***"
        } else {
            sigdf[index,"p.signif"] <- "ns"
        }
        
        index=index+1
    }
    firstdf$Weekday <- factor(firstdf$Weekday, levels = firstdf$Weekday) #ensures weekdays stay in order Sun-Sat
    seconddf$Weekday <- factor(seconddf$Weekday, levels = seconddf$Weekday) #ensures weekdays stay in order Sun-Sat
    comparedf <- rbind(firstdf,seconddf)
    
    #To add significance markers can try method here: https://www.r-bloggers.com/add-p-values-and-significance-levels-to-ggplots/
    #library(ggpubr)
    
    require(ggplot2)
    png(paste("Comparison between ",wkone," and ",wktwo,".png",sep=""), 
        width = 9, 
        height = 6, 
        units = 'in', 
        bg = "transparent", 
        res = 300)
    print(ggplot(comparedf, aes(x=Weekday, y=Mean_Sz_count, fill=Week)) + 
        geom_bar(position=position_dodge(), stat="identity",
                 colour="black", # Use black outlines,
                 size=.3) +      # Thinner lines
        #stat_compare_means(aes(group = Week), label = "p.signif", label.y = 300)
        geom_errorbar(aes(ymin=Mean_Sz_count-se, ymax=Mean_Sz_count+se),
                      size=.3,    # Thinner lines
                      width=.2,
                      position=position_dodge(.9)) +
        xlab("Weekday") +
        ylab("Number of seizures (\u00b1SEM)") +
        scale_fill_hue(name=paste(wkone,"vs",wktwo), # Legend label, use darker colors
                       breaks=c(wkone, wktwo),
                       labels=c(wkone, wktwo)) +
        ggtitle("Comparison of seizures on a given weekday") +
        scale_y_continuous(breaks=0:500*100) +
        theme_bw())
    dev.off()
    
    print(sigdf)
    write.table(sigdf,file=paste("T-tests between ",wkone," and ",wktwo,".txt",sep=""),quote = F,row.names = F)
###Prior compareweeks function (first function contents)###
```